---
title: "CalCOFI Tow Plotting"
author: "Zack Gold"
date: "2024-06-18"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```


```{r, echo=FALSE, hide=TRUE, warnings=FALSE,message=FALSE}
library(tidyverse)
library(here)
library(sf)
library(devtools)
library(nationalparkcolors)
library(knitr)
library("rnaturalearth")
library("rnaturalearthdata")
library("readxl")
library(parzer)
library(lubridate)
library(tinytex)

world <- ne_countries(scale = "medium", returnclass = "sf")

```

```{r,echo=FALSE, hide=TRUE, warnings=FALSE,message = FALSE}

tow_type <- read_csv(here("erddap_calcofi","erdCalCOFItowtyp_151f_ab30_5792.csv"))

tow_data <- read_csv(here("erddap_calcofi","erdCalCOFItows_8411_77f5_5500.csv"))

tow_data %>% 
  left_join(tow_type) %>% 
  slice(-1) %>% 
  mutate(., time=ymd_hms(time),
         year= year(time),
        month= month(time),
        season = case_when(month < 3 ~"Winter",
                           month < 6 ~"Spring",
                           month < 9 ~"Summer",
                           month < 12 ~"Fall",
                           TRUE ~"Winter")) %>% 
  mutate(., latitude= as.numeric(latitude),
         longitude = as.numeric(longitude),
         Lon_deg_r=round(longitude,1),
          Lat_deg_r=round(latitude,1)) %>% 
  mutate(., site= str_c(line,"_",station),
         year_site = str_c(year,":",line,"_",station),
         year_season_site = str_c(year,":",season,line,"_",station)) %>% 
  filter(., year > 1995) %>% 
  filter(., year != 1997) %>% 
  filter(., tow_type =="CB") -> calcofi_tows_all


calcofi_tows_all %>%  
  group_by(`site`) %>% 
  count() %>% 
  arrange(desc(n)) %>% 
  filter(., n > 5) -> unique_stations_to_keep_all


calcofi_tows_all %>% 
  filter(., Lat_deg_r > 31) %>% 
  filter(., Lat_deg_r < 35) %>% 
  filter(., !line %in% c(76.7, 70.0,73.3)) %>% 
  filter(., season %in% c("Spring", "Fall"))-> calcofi_tows_spring_fall

calcofi_tows_spring_fall %>%  
  group_by(`site`) %>% 
  count() %>% 
  arrange(desc(n)) %>% 
  filter(., n > 5) -> unique_stations_to_keep

calcofi_tows_spring_fall %>% 
  filter(., site %in% unique_stations_to_keep$site) -> calcofi_tows_spring_fall

calcofi_tows_all %>% 
  filter(., site %in% unique_stations_to_keep_all$site) -> calcofi_tows_all

```

```{r, warnings=FALSE,echo=FALSE, hide=TRUE, warnings=FALSE,message = FALSE}
#make some colors


pal <- park_palette("Denali", 5)
pal2 <- park_palette("Yellowstone", 5)

pal3 <- park_palette("Arches", 5)
pal4 <- park_palette("Hawaii", 5)
```

# Map of All  Stations
## General Statistics

### Unique Samples, Cruises, and Sites:
```{r,echo=FALSE}

calcofi_tows_all %>% 
dplyr::summarise(n_distinct(cruise), n_distinct(`site`), n_distinct(`year_season_site`)) %>%  kable()

```

This is an optimistic number based on the event records for formalin preserved net tows. Likely not all of these samples exist.

# Map of All Stations

```{r,echo=FALSE,warning=FALSE,message=FALSE, fig.width=12,fig.height=6 }

min_lat <- min(calcofi_tows_all$Lat_deg_r)
max_lat <- max(calcofi_tows_all$Lat_deg_r)

min_lon <- min(calcofi_tows_all$Lon_deg_r)
max_lon <- max(calcofi_tows_all$Lon_deg_r)

calcofi_tows_all$year <- as.character(calcofi_tows_all$year)

calcofi_tows_all %>% 
  select(year, season, site) %>% 
  group_by(site, season) %>% 
  count() -> group_by_site_all

calcofi_tows_all %>% 
  dplyr::select(site, season, Lat_deg_r, Lon_deg_r) %>% 
  distinct() -> lat_lot_back_all

lat_lot_back_all %>% 
  group_by(site, season) %>% 
  slice(1) ->lat_lot_back_all

group_by_site_all %>% 
  left_join(lat_lot_back_all) -> group_by_site_all

ggplot(data = world) +
    geom_sf() +
    geom_point(data = group_by_site_all, aes(x = Lon_deg_r, y = Lat_deg_r, size=n,colour=n),alpha=0.6 ) +
    coord_sf(xlim = c(min_lon-1, max_lon+1), ylim = c(min_lat-0.5, max_lat+0.5), expand = FALSE) +theme_bw() +xlab("Longitude") +ylab("Latitude") +facet_wrap(.~season, ncol=2) +scale_colour_viridis_c(option = "magma", direction=-1)+ theme(plot.title = element_text(hjust = 0.5,size = 20, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5,size = 18, face = "bold"),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.text=element_text(size=12), 
        strip.text = element_text(size=16, face="bold"), 
        axis.title=element_text(size=16,face="bold"),
        legend.title = element_text( size=16, face="bold"),
        legend.text = element_text(size=14)
        ) -> figure_1

figure_1

```

Spring and Winter sampling is more consistent and extends further north. Spring, at least for ichthyoplankton, is the time of the highest observed diversity coinciding with peak spawning for many species. 

# Focus on Southern California Bight Spring & Fall

## General Statistics


### Unique Samples, Cruises, and Sites:

```{r,echo=FALSE}

calcofi_tows_spring_fall %>% 
dplyr::summarise(n_distinct(`year_site`), n_distinct(cruise), n_distinct(`site`), n_distinct(`year_season_site`)) %>%  kable()

```

## Sampling Distribution of Samples:

```{r,echo=FALSE,warning=FALSE, message=FALSE, fig.width=16,fig.height=12 }
my_binwidth <- 1

calcofi_tows_spring_fall %>%  
  group_by(`site`,season) %>% 
  ggplot(., aes(x=`site`))+
  geom_histogram(binwidth = my_binwidth, colour= "black", fill = pal[1], stat = "count") +theme_bw()  +ylab("Number of Samples") + xlab("Stations") + facet_wrap(.~season, ncol=1) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size= 12, face = "bold"), axis.title =element_text(size=22, face = "bold"),
        axis.text.y = element_text(size=20, hjust = 1, face = "bold"),
        legend.text = element_text(size = 18, face = "bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        strip.text = element_text(size=22, face="bold"))


```

<div style="page-break-after: always; visibility: hidden"> 
\pagebreak 
</div>


# Zack's Selected Priority Sampling - Coastal Focus 1996-2023

n=1212 tows x2 seasons

## Main Target: Southern California Bight Coastal Eutriphication Driven Hypoxia

The focus is on the coastal grid capturing areas inside and outside the reoccurring hypoxic eddy centered south of Santa Catalina Island. Capturing 25 years of sampling including multiple El Niño and La Niñas, marine heat waves, and documented regime shifts in ichthyoplankton (notably tropicalization of southern mesopelagic species). 

## Secondary Targets: National Marine Sanctuaries & Wind Lease Areas

Capturing Spring data from further North provides baseline data inside and outside of the Channel Islands NMS, proposed Chumash Heritage NMS, and the Morro Bay Wind Lease Area. This also captures inshore state waters supporting OPC, CDFW, and SCCOOS priorities.

There is a diminished focus on the offshore stations, but hopefully still enough spatial and temporal scale to provide regional resolution.

This set up also lends itself to systematic  partitioning of the work. On average there are ~27 jars per cruise and so can process 3-4 jars per batch. Can also focus on all Spring samples first and then decide to expand to Fall sampling as a second set. 
 

*Summary Table*
```{r, echo=FALSE,warning=FALSE, message=FALSE}

subset_8_specific_stations = c(
"70_51","70_55", "70_60","70_80",
"73.3_50","73.3_55","73.3_60","73.3_80",
"76.7_49","76.7_55","76.7_60","76.8_60",
"80_50.5","80_55","80_60", "80_80",
"81.7_43.5", "81.8_46.9",
"83.3_51", "83.3_40.6", "83.3_39.4","83.3_55",
"86.7_45", "86.7_33","86.7_40",
"90_45","90_37", "90_35", "90_28","90_60",
"93.3_30", "93.3_26.7","93.4_26.4","93.3_40","93.3_35",
"85.4_35.8", "86.8_32.5", "88.5_30.1", "91.7_26.4" )

#calcofi_tows_all$site %>%  unique() %>%  sort()
calcofi_tows_all %>% 
  filter(., site %in% subset_8_specific_stations)  %>% 
  filter(., season %in% c("Spring", "Fall"))-> calcofi_tows_a8


calcofi_tows_a8 %>% 
dplyr::summarise(n_distinct(`year_season_site`),n_distinct(`year_site`), n_distinct(cruise), n_distinct(`site`))  %>%  kable()
```
*Average Samples per Cruise*
```{r}
calcofi_tows_a8 %>% 
  ungroup() %>% 
  group_by(cruise) %>% 
  count() %>% 
  ungroup() %>% 
dplyr::summarise(mean(n), max(n), min(n))  %>%  kable()

```


```{r, echo=FALSE,warning=FALSE, message=FALSE}
calcofi_tows_a8 %>% 
  select(year, season, site) %>% 
  group_by(site, season) %>% 
  count() -> group_by_site_f_a8

calcofi_tows_all %>% 
  dplyr::select(site, season, Lat_deg_r, Lon_deg_r) %>% 
  distinct() -> lat_lot_back_all

lat_lot_back_all %>% 
  group_by(site, season) %>% 
  slice(1) ->lat_lot_back_all

group_by_site_f_a8 %>% 
  left_join(lat_lot_back_all) -> group_by_site_f_a8


```

### Map of Selected Sites

```{r, echo=FALSE,warning=FALSE, message=FALSE, fig.width=12}

min_lat <- min(group_by_site_f_a8$Lat_deg_r)
max_lat <- max(group_by_site_f_a8$Lat_deg_r)

min_lon <- min(group_by_site_f_a8$Lon_deg_r)
max_lon <- max(group_by_site_f_a8$Lon_deg_r)


ggplot(data = world) +
    geom_sf() +
    geom_point(data = group_by_site_f_a8, aes(x = Lon_deg_r, y = Lat_deg_r, size=n,colour=n),alpha=0.6 ) +
    coord_sf(xlim = c(min_lon-1, max_lon+1), ylim = c(min_lat-0.5, max_lat+0.5), expand = FALSE) +theme_bw() +xlab("Longitude") +ylab("Latitude") +facet_grid(.~season) +scale_colour_viridis_c(option = "magma", direction=-1) + theme(plot.title = element_text(hjust = 0.5,size = 20, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5,size = 18, face = "bold"),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.text=element_text(size=12), 
        strip.text = element_text(size=16, face="bold"), 
        axis.title=element_text(size=16,face="bold"),
        legend.title = element_text( size=16, face="bold"),
        legend.text = element_text(size=14)
        )-> option8

option8

```











