---
title: "CalCOFI Tow Plotting"
author: "Zack Gold"
date: "2024-03-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r, echo=FALSE, hide=TRUE, warnings=FALSE,message=FALSE}
library(tidyverse)
library(here)
library(sf)
library(devtools)
library(nationalparkcolors)
library(knitr)
library("rnaturalearth")
library("rnaturalearthdata")
library("readxl")
library(parzer)
library(lubridate)

world <- ne_countries(scale = "medium", returnclass = "sf")

```

```{r,echo=FALSE, hide=TRUE, warnings=FALSE,message = FALSE}

tow_type <- read_csv(here("erddap_calcofi","erdCalCOFItowtyp_151f_ab30_5792.csv"))

tow_data <- read_csv(here("erddap_calcofi","erdCalCOFItows_8411_77f5_5500.csv"))

tow_data %>% 
  left_join(tow_type) %>% 
  slice(-1) %>% 
  mutate(., time=ymd_hms(time),
         year= year(time),
        month= month(time),
        season = case_when(month < 3 ~"Winter",
                           month < 6 ~"Spring",
                           month < 8 ~"Summer",
                           month < 12 ~"Fall",
                           TRUE ~"Winter")) %>% 
  mutate(., latitude= as.numeric(latitude),
         longitude = as.numeric(longitude),
         Lon_deg_r=round(longitude,1),
          Lat_deg_r=round(latitude,1)) %>% 
  mutate(., site= str_c(line,"_",station),
         year_site = str_c(year,":",line,"_",station),
         year_season_site = str_c(year,":",season,line,"_",station)) %>% 
  filter(., year > 1995) %>% 
  filter(., year != 1997) %>% 
  filter(., tow_type =="CB") -> calcofi_tows_all


calcofi_tows_all %>%  
  group_by(`site`) %>% 
  count() %>% 
  arrange(desc(n)) %>% 
  filter(., n > 5) -> unique_stations_to_keep_all


calcofi_tows_all %>% 
  filter(., Lat_deg_r > 31) %>% 
  filter(., Lat_deg_r < 35) %>% 
  filter(., !line %in% c(76.7, 70.0,73.3)) %>% 
  filter(., season %in% c("Spring", "Fall"))-> calcofi_tows

calcofi_tows %>%  
  group_by(`site`) %>% 
  count() %>% 
  arrange(desc(n)) %>% 
  filter(., n > 5) -> unique_stations_to_keep

calcofi_tows %>% 
  filter(., site %in% unique_stations_to_keep$site) -> calcofi_tows

calcofi_tows_all %>% 
  filter(., site %in% unique_stations_to_keep_all$site) -> calcofi_tows_all

```

```{r, warnings=FALSE,echo=FALSE, hide=TRUE, warnings=FALSE,message = FALSE}
#make some colors


pal <- park_palette("Denali", 5)
pal2 <- park_palette("Yellowstone", 5)

pal3 <- park_palette("Arches", 5)
pal4 <- park_palette("Hawaii", 5)
```

# Map of All  Stations
## General Statistics

### Unique Samples, Cruises, and Sites:
```{r,echo=FALSE}

calcofi_tows_all %>% 
dplyr::summarise(n_distinct(`year_site`), n_distinct(cruise), n_distinct(`site`), n_distinct(`year_season_site`)) %>%  kable()

```

## Sampling Distribution of Samples:

```{r,echo=FALSE, hide=TRUE, warnings=FALSE,message=FALSE}
my_binwidth <- 1

calcofi_tows_all %>%  
  group_by(`site`,season) %>% 
  ggplot(., aes(x=`site`))+
  geom_histogram(binwidth = my_binwidth, colour= "black", fill = pal[1], stat = "count") +theme_bw()  +xlab("Number of Samples") + ylab("Count") + facet_wrap(.~season, ncol=2) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


```

## Heatmap of Sampling Intensity


```{r,echo=FALSE,warning=FALSE, warnings=FALSE,message=FALSE, fig.width=12, fig.height=20}

calcofi_tows_all %>% 
  select(line,station, year, season) %>% 
  mutate(., line= as.character(line),
         station=as.character(station)) %>% 
  group_by(line,station, season) %>% 
  count() %>% 
  mutate(., `Distinct Times Sample`=n) %>% 
  mutate(., site= str_c(line,"_",station)) %>% 
  ggplot(., aes(x=`Distinct Times Sample`, y= site, color=`Distinct Times Sample`, fill=`Distinct Times Sample`)) +geom_tile() +facet_grid(.~season) +scale_color_viridis_c() +scale_fill_viridis_c()


```

# Map of All Stations

```{r,echo=FALSE,warning=FALSE,message=FALSE, fig.height= 8, fig.width= 12}

min_lat <- min(calcofi_tows_all$Lat_deg_r)
max_lat <- max(calcofi_tows_all$Lat_deg_r)

min_lon <- min(calcofi_tows_all$Lon_deg_r)
max_lon <- max(calcofi_tows_all$Lon_deg_r)

calcofi_tows_all$year <- as.character(calcofi_tows_all$year)

calcofi_tows_all %>% 
  select(year, season, site) %>% 
  group_by(site, season) %>% 
  count() -> group_by_site_all

calcofi_tows_all %>% 
  dplyr::select(site, season, Lat_deg_r, Lon_deg_r) %>% 
  distinct() -> lat_lot_back_all

lat_lot_back_all %>% 
  group_by(site, season) %>% 
  slice(1) ->lat_lot_back_all

group_by_site_all %>% 
  left_join(lat_lot_back_all) -> group_by_site_all

ggplot(data = world) +
    geom_sf() +
    geom_point(data = group_by_site_all, aes(x = Lon_deg_r, y = Lat_deg_r, size=n,colour=n),alpha=0.6 ) +
    coord_sf(xlim = c(min_lon-1, max_lon+1), ylim = c(min_lat-0.5, max_lat+0.5), expand = FALSE) +theme_bw() +xlab("Longitude") +ylab("Latitude") +facet_wrap(.~season, ncol=2) +scale_colour_viridis_c(option = "magma", direction=-1) #+ geom_text(data = group_by_site_all, aes(x = Lon_deg_r, y = Lat_deg_r, label=site),size = 4)

```

# Focus on Southern California Bight Spring & Fall

## General Statistics


### Unique Samples, Cruises, and Sites:

```{r,echo=FALSE}

calcofi_tows %>% 
dplyr::summarise(n_distinct(`year_site`), n_distinct(cruise), n_distinct(`site`), n_distinct(`year_season_site`)) %>%  kable()

```

## Sampling Distribution of Samples:

```{r,echo=FALSE,warning=FALSE, message=FALSE, fig.width=16,fig.height=12 }
my_binwidth <- 1

calcofi_tows %>%  
  group_by(`site`,season) %>% 
  ggplot(., aes(x=`site`))+
  geom_histogram(binwidth = my_binwidth, colour= "black", fill = pal[1], stat = "count") +theme_bw()  +xlab("Number of Samples") + ylab("Count") + facet_grid(.~season) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


```



## Heatmap of Sampling Intensity

```{r,echo=FALSE,warning=FALSE,message=FALSE, fig.width=12,fig.height=20}

calcofi_tows %>% 
  select(line,station, year, season) %>% 
  mutate(., line= as.character(line),
         station=as.character(station)) %>% 
  group_by(line,station, season) %>% 
  count() %>% 
  mutate(., `Distinct Years Sample`=n) %>% 
  mutate(., site= str_c(line,"_",station)) %>% 
  ggplot(., aes(x=`Distinct Years Sample`, y= site, color=`Distinct Years Sample`, fill=`Distinct Years Sample`)) +geom_tile() +facet_grid(.~season) +scale_color_viridis_c() +scale_fill_viridis_c()


```
  




# Map of All Relevant Stations

```{r,echo=FALSE,warning=FALSE, message=FALSE, fig.width=12}

min_lat <- min(calcofi_tows$Lat_deg_r)
max_lat <- max(calcofi_tows$Lat_deg_r)

min_lon <- min(calcofi_tows$Lon_deg_r)
max_lon <- max(calcofi_tows$Lon_deg_r)

calcofi_tows$year <- as.character(calcofi_tows$year)

calcofi_tows %>% 
  select(year, season, site) %>% 
  group_by(site, season) %>% 
  count() -> group_by_site

calcofi_tows %>% 
  dplyr::select(site, season, Lat_deg_r, Lon_deg_r) %>% 
  distinct() -> lat_lot_back

lat_lot_back %>% 
  group_by(site, season) %>% 
  slice(1) ->lat_lot_back

group_by_site %>% 
  left_join(lat_lot_back) -> group_by_site

ggplot(data = world) +
    geom_sf() +
    geom_point(data = group_by_site, aes(x = Lon_deg_r, y = Lat_deg_r, size=n,colour=n),alpha=0.6 ) +
    coord_sf(xlim = c(min_lon-1, max_lon+1), ylim = c(min_lat-0.5, max_lat+0.5), expand = FALSE) +theme_bw() +xlab("Longitude") +ylab("Latitude") +facet_grid(.~season) +scale_colour_viridis_c(option = "magma", direction=-1) 
#+ geom_text(data = group_by_site, aes(x = Lon_deg_r, y = Lat_deg_r, label=site),size = 4)

```

# Subset 1 Coastal More Recent
## Only Choose Stations East of 120W from 2010-2019
n=529 tows x2 seasons
```{r,echo=FALSE,warning=FALSE, message=FALSE}

calcofi_tows %>% 
  filter(., year > 2009) %>% 
   filter(., year < 2021) %>% 
  filter(., Lon_deg_r > -120.1) -> calcofi_tows_a1


calcofi_tows_a1 %>% 
dplyr::summarise(n_distinct(`year_season_site`),n_distinct(`year_site`), n_distinct(cruise), n_distinct(`site`))  %>%  kable()
```

```{r, echo=FALSE,warning=FALSE, message=FALSE}
calcofi_tows_a1 %>% 
  select(year, season, site) %>% 
  group_by(site, season) %>% 
  count() -> group_by_site_f_a1

group_by_site_f_a1 %>% 
  left_join(lat_lot_back) -> group_by_site_f_a1


```

```{r,echo=FALSE,warning=FALSE, message=FALSE, fig.width=12}

min_lat <- min(group_by_site_f_a1$Lat_deg_r)
max_lat <- max(group_by_site_f_a1$Lat_deg_r)

min_lon <- min(group_by_site_f_a1$Lon_deg_r)
max_lon <- max(group_by_site_f_a1$Lon_deg_r)


ggplot(data = world) +
    geom_sf() +
    geom_point(data = group_by_site_f_a1, aes(x = Lon_deg_r, y = Lat_deg_r, size=n,colour=n),alpha=0.6 ) +
    coord_sf(xlim = c(min_lon-1, max_lon+1), ylim = c(min_lat-0.5, max_lat+0.5), expand = FALSE) +theme_bw() +xlab("Longitude") +ylab("Latitude") +facet_grid(.~season) +scale_colour_viridis_c(option = "magma", direction=-1)

```

# Subset 2 Coastal Full Time
## Only Choose Coastal Stations 1996-2023
n=921 tows x2 seasons
```{r,echo=FALSE,warning=FALSE, message=FALSE}

subset_2_specific_stations = c( 
  "93.4_26.4", "93.3_26.7", "93.3_28",   "93.3_30",   "93.3_35",   "93.3_40",   
  "90_45"    ,"90_37"   ,  "90_35"  ,   "90_30"   ,  "90_28"   , "90_27.7", "86.7_33"   ,"86.7_35" ,  "86.7_40" ,  "86.7_45" , "86.7_50" ,  
  "83.3_42" ,  "83.3_40.6" ,    "83.3_39.4",
"88.5_30.1",
"85.4_35.8",
"86.8_32.5",
"91.7_26.4")

calcofi_tows %>% 
  filter(., site %in% subset_2_specific_stations)  -> calcofi_tows_a2


calcofi_tows_a2 %>% 
dplyr::summarise(n_distinct(`year_season_site`),n_distinct(`year_site`), n_distinct(cruise), n_distinct(`site`))  %>%  kable()
```

```{r, echo=FALSE,warning=FALSE, message=FALSE}
calcofi_tows_a2 %>% 
  select(year, season, site) %>% 
  group_by(site, season) %>% 
  count() -> group_by_site_f_a2

group_by_site_f_a2 %>% 
  left_join(lat_lot_back) -> group_by_site_f_a2


```

```{r, echo=FALSE,warning=FALSE, message=FALSE, fig.width=12}

min_lat <- min(group_by_site_f_a2$Lat_deg_r)
max_lat <- max(group_by_site_f_a2$Lat_deg_r)

min_lon <- min(group_by_site_f_a2$Lon_deg_r)
max_lon <- max(group_by_site_f_a2$Lon_deg_r)


ggplot(data = world) +
    geom_sf() +
    geom_point(data = group_by_site_f_a2, aes(x = Lon_deg_r, y = Lat_deg_r, size=n,colour=n),alpha=0.6 ) +
    coord_sf(xlim = c(min_lon-1, max_lon+1), ylim = c(min_lat-0.5, max_lat+0.5), expand = FALSE) +theme_bw() +xlab("Longitude") +ylab("Latitude") +facet_grid(.~season) +scale_colour_viridis_c(option = "magma", direction=-1)  

```

# Subset 3 Wider Coastal Grid Full Time
## Only Choose Coastal Stations 1996-2023
n=782 tows x2 seasons
```{r,echo=FALSE,warning=FALSE, message=FALSE}

subset_3_specific_stations = c( "80_50.5"  ,   "80_60"   ,
"81.7_43.5", "81.8_46.9",
"83.3_39.4",   "83.3_51",   "83.3_60",  
"85.4_35.8",    "86.7_35",  "86.7_40", "86.7_60",
"86.8_32.5",
"88.5_30.1",
"90_27.7" , "90_35" ,  "90_45",  "90_60", 
"91.7_26.4", "93.3_28",    "93.3_35" ,  "93.3_45",  "93.4_26.4")

calcofi_tows %>% 
  filter(., site %in% subset_3_specific_stations)  -> calcofi_tows_a3


calcofi_tows_a3 %>% 
dplyr::summarise(n_distinct(`year_season_site`),n_distinct(`year_site`), n_distinct(cruise), n_distinct(`site`))  %>%  kable()
```

```{r, echo=FALSE,warning=FALSE, message=FALSE}
calcofi_tows_a3 %>% 
  select(year, season, site) %>% 
  group_by(site, season) %>% 
  count() -> group_by_site_f_a3

group_by_site_f_a3 %>% 
  left_join(lat_lot_back) -> group_by_site_f_a3


```

```{r, echo=FALSE,warning=FALSE, message=FALSE, fig.width=12}

min_lat <- min(group_by_site_f_a3$Lat_deg_r)
max_lat <- max(group_by_site_f_a3$Lat_deg_r)

min_lon <- min(group_by_site_f_a3$Lon_deg_r)
max_lon <- max(group_by_site_f_a3$Lon_deg_r)


ggplot(data = world) +
    geom_sf() +
    geom_point(data = group_by_site_f_a3, aes(x = Lon_deg_r, y = Lat_deg_r, size=n,colour=n),alpha=0.6 ) +
    coord_sf(xlim = c(min_lon-1, max_lon+1), ylim = c(min_lat-0.5, max_lat+0.5), expand = FALSE) +theme_bw() +xlab("Longitude") +ylab("Latitude") +facet_grid(.~season) +scale_colour_viridis_c(option = "magma", direction=-1)  

```

# Subset 4 Narrow Coastal Grid Full Time
## Only Choose Coastal Stations 1996-2023
n=750 tows x2 seasons
```{r, echo=FALSE,warning=FALSE, message=FALSE}

subset_3_specific_stations = c( "80_50.5"  ,   "80_50.5"   ,
"81.7_43.5", "81.8_46.9",
"83.3_39.4",   "83.3_51",   "83.3_40.6",  
"85.4_35.8",    "86.7_35",  "86.7_40", "86.7_33",
"86.8_32.5",
"88.5_30.1",
"90_27.7" , "90_35" ,  "90_45",  "90_30", 
"91.7_26.4", "93.3_28",    "93.3_35" ,  "93.3_30",  "93.4_26.4")

calcofi_tows %>% 
  filter(., site %in% subset_3_specific_stations)  -> calcofi_tows_a4


calcofi_tows_a4 %>% 
dplyr::summarise(n_distinct(`year_season_site`),n_distinct(`year_site`), n_distinct(cruise), n_distinct(`site`))  %>%  kable()
```

```{r, echo=FALSE,warning=FALSE, message=FALSE}
calcofi_tows_a4 %>% 
  select(year, season, site) %>% 
  group_by(site, season) %>% 
  count() -> group_by_site_f_a4

group_by_site_f_a4 %>% 
  left_join(lat_lot_back) -> group_by_site_f_a4


```

```{r, echo=FALSE,warning=FALSE, message=FALSE, fig.width=12}

min_lat <- min(group_by_site_f_a4$Lat_deg_r)
max_lat <- max(group_by_site_f_a4$Lat_deg_r)

min_lon <- min(group_by_site_f_a4$Lon_deg_r)
max_lon <- max(group_by_site_f_a4$Lon_deg_r)


ggplot(data = world) +
    geom_sf() +
    geom_point(data = group_by_site_f_a4, aes(x = Lon_deg_r, y = Lat_deg_r, size=n,colour=n),alpha=0.6 ) +
    coord_sf(xlim = c(min_lon-1, max_lon+1), ylim = c(min_lat-0.5, max_lat+0.5), expand = FALSE) +theme_bw() +xlab("Longitude") +ylab("Latitude") +facet_grid(.~season) +scale_colour_viridis_c(option = "magma", direction=-1)  

```

# Subset 5 Narrow Southern Coastal Grid Full Time
## Only Choose Coastal Stations 1996-2023
n=750 tows x2 seasons
```{r, echo=FALSE,warning=FALSE, message=FALSE}

subset_5_specific_stations = c( 
"86.7_33",    "86.7_35","85.4_35.8",  "86.7_40" ,"86.7_45","86.7_50",
"86.8_32.5",
"88.5_30.1",
"90_27.7" , "90_28", "90_30", "90_35" , "90_37", "90_45",   
"91.7_26.4", "93.4_26.4","93.3_28",  "93.3_30",  "93.3_35" ,  "93.3_40" )

calcofi_tows %>% 
  filter(., site %in% subset_5_specific_stations)  -> calcofi_tows_a5


calcofi_tows_a5 %>% 
dplyr::summarise(n_distinct(`year_season_site`),n_distinct(`year_site`), n_distinct(cruise), n_distinct(`site`))  %>%  kable()
```

```{r, echo=FALSE,warning=FALSE, message=FALSE}
calcofi_tows_a5 %>% 
  select(year, season, site) %>% 
  group_by(site, season) %>% 
  count() -> group_by_site_f_a5

group_by_site_f_a5 %>% 
  left_join(lat_lot_back) -> group_by_site_f_a5


```

```{r, echo=FALSE,warning=FALSE, message=FALSE, fig.width=12}

min_lat <- min(group_by_site_f_a5$Lat_deg_r)
max_lat <- max(group_by_site_f_a5$Lat_deg_r)

min_lon <- min(group_by_site_f_a5$Lon_deg_r)
max_lon <- max(group_by_site_f_a5$Lon_deg_r)


ggplot(data = world) +
    geom_sf() +
    geom_point(data = group_by_site_f_a5, aes(x = Lon_deg_r, y = Lat_deg_r, size=n,colour=n),alpha=0.6 ) +
    coord_sf(xlim = c(min_lon-1, max_lon+1), ylim = c(min_lat-0.5, max_lat+0.5), expand = FALSE) +theme_bw() +xlab("Longitude") +ylab("Latitude") +facet_grid(.~season) +scale_colour_viridis_c(option = "magma", direction=-1)  

```

# Subset 6 WCOA Linked Southern Coastal Grid Full Time
## Only Choose Coastal Stations 1996-2023
n=1267 tows x2 seasons
```{r, echo=FALSE,warning=FALSE, message=FALSE}

subset_6_specific_stations = c(
"80_60","80_70","80_80","80_55", "80_51", "80_50.5",
"93.3_35", "93.3_30", "93.3_26.7","93.4_26.4","93.3_40",
"83.3_51", "81.8_46.9", "83.3_40.6",
"86.7_45", "86.7_33","86.7_35","86.7_40",
"90_45", "90_35", "90_28","90_27.7", "90_30","90_37","90_53","90_60","90_70",
"81.7_43.5", 
"83.3_39.4", 
"85.4_35.8", "86.8_32.5", "88.5_30.1", "91.7_26.4" )

calcofi_tows %>% 
  filter(., site %in% subset_6_specific_stations)  -> calcofi_tows_a6


calcofi_tows_a6 %>% 
dplyr::summarise(n_distinct(`year_season_site`),n_distinct(`year_site`), n_distinct(cruise), n_distinct(`site`))  %>%  kable()
```

```{r, echo=FALSE,warning=FALSE, message=FALSE}
calcofi_tows_a6 %>% 
  select(year, season, site) %>% 
  group_by(site, season) %>% 
  count() -> group_by_site_f_a6

group_by_site_f_a6 %>% 
  left_join(lat_lot_back) -> group_by_site_f_a6


```

```{r, echo=FALSE,warning=FALSE, message=FALSE, fig.width=12}

min_lat <- min(group_by_site_f_a6$Lat_deg_r)
max_lat <- max(group_by_site_f_a6$Lat_deg_r)

min_lon <- min(group_by_site_f_a6$Lon_deg_r)
max_lon <- max(group_by_site_f_a6$Lon_deg_r)


ggplot(data = world) +
    geom_sf() +
    geom_point(data = group_by_site_f_a6, aes(x = Lon_deg_r, y = Lat_deg_r, size=n,colour=n),alpha=0.6 ) +
    coord_sf(xlim = c(min_lon-1, max_lon+1), ylim = c(min_lat-0.5, max_lat+0.5), expand = FALSE) +theme_bw() +xlab("Longitude") +ylab("Latitude") +facet_grid(.~season) +scale_colour_viridis_c(option = "magma", direction=-1)  

```

# Subset 7 WCOA Linked Southern Coastal Grid Full Time

## Only Choose Coastal Stations 1996-2023

n=780 tows x2 seasons

```{r, echo=FALSE,warning=FALSE, message=FALSE}

subset_7_specific_stations = c(
"80_80","80_55", "80_50.5",
"93.3_30", "93.3_26.7","93.4_26.4","93.3_40",
"83.3_51", "83.3_40.6", "83.3_39.4",
"86.7_45", "86.7_33","86.7_40",
"90_45","90_40", "90_35", "90_28","90_60",
"85.4_35.8", "86.8_32.5", "88.5_30.1", "91.7_26.4" )

calcofi_tows %>% 
  filter(., site %in% subset_7_specific_stations)  -> calcofi_tows_a7


calcofi_tows_a7 %>% 
dplyr::summarise(n_distinct(`year_season_site`),n_distinct(`year_site`), n_distinct(cruise), n_distinct(`site`))  %>%  kable()
```

```{r, echo=FALSE,warning=FALSE, message=FALSE}
calcofi_tows_a7 %>% 
  select(year, season, site) %>% 
  group_by(site, season) %>% 
  count() -> group_by_site_f_a7

group_by_site_f_a7 %>% 
  left_join(lat_lot_back) -> group_by_site_f_a7


```

```{r, echo=FALSE,warning=FALSE, message=FALSE, fig.width=12}

min_lat <- min(group_by_site_f_a7$Lat_deg_r)
max_lat <- max(group_by_site_f_a7$Lat_deg_r)

min_lon <- min(group_by_site_f_a7$Lon_deg_r)
max_lon <- max(group_by_site_f_a7$Lon_deg_r)


ggplot(data = world) +
    geom_sf() +
    geom_point(data = group_by_site_f_a7, aes(x = Lon_deg_r, y = Lat_deg_r, size=n,colour=n),alpha=0.6 ) +
    coord_sf(xlim = c(min_lon-1, max_lon+1), ylim = c(min_lat-0.5, max_lat+0.5), expand = FALSE) +theme_bw() +xlab("Longitude") +ylab("Latitude") +facet_grid(.~season) +scale_colour_viridis_c(option = "magma", direction=-1) # + geom_text(data = group_by_site_f_a7, aes(x = Lon_deg_r, y = Lat_deg_r, label=site),size = 4)


```

# Subset 8 NMS + SoCal
## Only Choose Coastal Stations 1996-2023
n=1260 tows x2 seasons
```{r, echo=FALSE,warning=FALSE, message=FALSE}

subset_8_specific_stations = c(
"70_51","70_55", "70_60","70_80",
"73.3_50","73.3_55","73.3_60","73.3_80",
"76.7_49","76.7_55","76.7_60","76.8_60",
"80_50.5","80_55","80_60", "80_80",
"81.7_43.5", "81.8_46.9",
"83.3_51", "83.3_40.6", "83.3_39.4","83.3_55",
"86.7_45", "86.7_33","86.7_40",
"90_45","90_37", "90_35", "90_28","90_60",
"93.3_30", "93.3_26.7","93.4_26.4","93.3_40","93.3_35",
"85.4_35.8", "86.8_32.5", "88.5_30.1", "91.7_26.4" )

#calcofi_tows_all$site %>%  unique() %>%  sort()
calcofi_tows_all %>% 
  filter(., site %in% subset_8_specific_stations)  %>% 
  filter(., season %in% c("Spring", "Fall"))-> calcofi_tows_a8


calcofi_tows_a8 %>% 
dplyr::summarise(n_distinct(`year_season_site`),n_distinct(`year_site`), n_distinct(cruise), n_distinct(`site`))  %>%  kable()
```

```{r, echo=FALSE,warning=FALSE, message=FALSE}
calcofi_tows_a8 %>% 
  select(year, season, site) %>% 
  group_by(site, season) %>% 
  count() -> group_by_site_f_a8

calcofi_tows_all %>% 
  dplyr::select(site, season, Lat_deg_r, Lon_deg_r) %>% 
  distinct() -> lat_lot_back_all

lat_lot_back_all %>% 
  group_by(site, season) %>% 
  slice(1) ->lat_lot_back_all

group_by_site_f_a8 %>% 
  left_join(lat_lot_back_all) -> group_by_site_f_a8


```

```{r, echo=FALSE,warning=FALSE, message=FALSE, fig.width=12}

min_lat <- min(group_by_site_f_a8$Lat_deg_r)
max_lat <- max(group_by_site_f_a8$Lat_deg_r)

min_lon <- min(group_by_site_f_a8$Lon_deg_r)
max_lon <- max(group_by_site_f_a8$Lon_deg_r)


ggplot(data = world) +
    geom_sf() +
    geom_point(data = group_by_site_f_a8, aes(x = Lon_deg_r, y = Lat_deg_r, size=n,colour=n),alpha=0.6 ) +
    coord_sf(xlim = c(min_lon-1, max_lon+1), ylim = c(min_lat-0.5, max_lat+0.5), expand = FALSE) +theme_bw() +xlab("Longitude") +ylab("Latitude") +facet_grid(.~season) +scale_colour_viridis_c(option = "magma", direction=-1) # + geom_text(data = group_by_site_f_a8, aes(x = Lon_deg_r, y = Lat_deg_r, label=site),size = 4)


```






