---
title: "Data Merging CalCOFI Krill + Bottles"
author: "Zack Gold"
date: "2024-07-30"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 

```

```{r, warning=FALSE, include=FALSE }
library(tidyverse)
library(here)
library(readxl)
library(knitr)
library(cmocean)
library(ggpubr)
library(ggpmisc)
library(sf)
library("rnaturalearth")
library("rnaturalearthdata")

world <- ne_countries(scale = "medium", returnclass = "sf")

```
# Import Data

## Load in the Krill Taxonomic File

```{r, echo=FALSE, hide=TRUE, warnings=FALSE,message=FALSE, include=FALSE}
#load in the Krill taxonomy data

BTEDB_tax <- read_xlsx(here("knb-lter-cce.313.1","BTEDB_tax.xlsx")) 

BTEDB_tax %>% 
  mutate(., Ohman_tax=str_remove(Ohman_tax,"_Abundance")) %>% #remove abundance tag
  separate(Ohman_tax, into=c("Genus","species","phase","type"), sep="_") %>%  #split name into components
  mutate(., type = replace_na(type, "")) %>%  #get rid of NAs
  mutate(ID_Microscopy=str_c(Genus,species, sep=" "), #pull together binomial name
         Phase=str_c(phase,type,sep="-")) %>%  #pull together phase
  dplyr::select(ID_Microscopy, Phase)%>%  
  distinct() -> visual_tax_names # make this distinct 
```

## Load in the Krill Count Data
```{r, echo=FALSE, hide=TRUE, warnings=FALSE,message=FALSE, include=FALSE}
# Load in the Brinton and Townsend Euphausiid Database - CCE-LTER
# aka krill
BTEDB <- read.csv(here("knb-lter-cce.313.1","BTEDB_Abundances.csv"))

# Pull in Ed Weber's awesome code to merge the Cast and Bottle Data
ed_key <- read.csv(here("data","20240612_key_ed_webber.csv"))

# Clean Up the Metadata
BTEDB %>%
  mutate(., PIC_RowNumber=RowNumber, # Clean Up Header
        TowBegin= as.POSIXct(TowBegin, format = "%Y-%m-%d %H:%M:%S"), # Fix Times
        TowEnd= as.POSIXct(TowEnd,  format = "%Y-%m-%d %H:%M:%S")) %>% # Fix Times
  pivot_longer(cols=`Euphausia_brevis_adult_Abundance`:`Thysanopoda_pectinata_juvenile_Abundance`,names_to = "Ohman_tax", values_to = "Count_permsq2") %>% 
  separate(Ohman_tax, into=c("Genus","species","phase","type"), sep="_", remove = F) %>% 
  mutate(., type = replace_na(type, "")) %>% 
  mutate(ID_Microscopy=str_c(Genus,species, sep=" "), 
         Phase=str_c(phase,type,sep="-")) %>% 
  dplyr::select(PIC_RowNumber,
Date,
MaxDepth,TowBegin,TowEnd,Ohman_tax,Genus,species, phase,type,Count_permsq2,ID_Microscopy,Phase
) %>% 
  left_join(ed_key)  %>%  # Note that there are missing Cast_Cnt values
  mutate(., Station = as.numeric(N_Station),
        Line = N_Line) %>% 
  filter(., N_lat > 27) %>% #There are some samples from around the world and we don't want them
  filter(., N_lat < 40) %>% 
  filter(., N_lon < -110) %>% 
   mutate(., site= str_c(N_Line,"_",N_Station),
         cruise_site = str_c(N_Cruise,":",N_Line,"_",N_Station))-> long_microscopy
# We will merge using cruise_site

  
```


## Most Frequently Counted Krill

```{r, echo=FALSE, hide=TRUE, warnings=FALSE,message=FALSE, fig.height=20, fig.width=20}

long_microscopy %>% 
  filter(., str_detect(Ohman_tax,"adult")) -> adult_data # focus on adult krill

long_microscopy %>% 
  filter(., Count_permsq2 > 0) %>% 
  ungroup() %>% 
  count(ID_Microscopy) %>% 
  arrange(desc(`n`)) %>% 
  filter(., n> 1000) -> abundant_species
  
abundant_species  %>% kable()

```
<div style="page-break-after: always; visibility: hidden"> 
\pagebreak 
</div>

## Load in the Bottle Data
```{r, echo=FALSE, hide=TRUE, warnings=FALSE,message=FALSE, include=FALSE}

bottle_data <- read.csv(here("data","CalCOFI_Database_194903-202105_csv","194903-202105_Bottle.csv"), header = T,check.names = F) #CTD bottle data

cast_data <- read.csv(here("data","CalCOFI_Database_194903-202105_csv","194903-202105_Cast.csv"), header = T,check.names = F) #CTD Cast data

cast_data %>% 
  left_join(bottle_data, relationship="many-to-many") -> cast_bottle

cast_bottle %>% 
  mutate(., Station = as.double(Rpt_Sta),
         Line = as.double(Rpt_Line),
         year=Year) %>% 
       mutate(., Date = as.Date(Date, "%m/%d/%Y"),
              year= year(Date),
        month= month(Date),
        season = case_when(month < 3 ~"Winter",
                           month < 6 ~"Spring",
                           month < 9 ~"Summer",
                           month < 12 ~"Fall",
                           TRUE ~"Winter")) %>% 
 mutate(., site= str_c(Line,"_",Station),
         year_site = str_c(year,":",Line,"_",Station),
         year_season_site = str_c(year,":",season,":",Line,"_",Station),
         cruise_site = str_c(Cruise,":",Line,"_",Station)) -> cast_bottle_fixed
# We will merge using cruise_site
  
```

# Full Merge Into Single Data
```{r}
adult_data %>% 
  left_join(cast_bottle_fixed, by=c("cruise_site"), relationship="many-to-many") %>% 
  filter(., ID_Microscopy %in% abundant_species$ID_Microscopy) -> adult_data_chem_full


```

# Interpolate Values

### Filter to the most recent casts
```{r}

#O2sat already calculated for recent data so ignoring this
#  mutate(O2meas = O2ml_L/31.9988/(STheta + 1000)*(1000^2),
#         O2sat = gsw_O2sol_SP_pt(Salnty, T_degC), SatPct = (O2meas/O2sat)*100) %>% 
#  relocate(c(O2meas, O2sat, SatPct), .after = O2ml_L)

cast_bottle_fixed %>% 
   filter(., year > 1993) -> cast_bottle_fixed_recent

cast_bottle_fixed_recent %>% 
  group_by(Cast_ID) %>% 
  dplyr::summarise(temp_na=sum(is.na(T_degC)),
                   sal_na=sum(is.na(Salnty)),
                   o2_na=sum(is.na(O2ml_L)),
                   sat_na=sum(is.na(O2Sat)),
                          tot=n()) %>% 
  filter(., temp_na < (tot-2) ) %>% 
  filter(., sal_na < (tot-2) ) %>% 
    filter(., o2_na < (tot-2) ) %>% 
    filter(., sat_na < (tot-2) )-> casts_to_keep

cast_bottle_fixed_recent %>% 
  filter(., Cast_ID %in% casts_to_keep$Cast_ID)-> cast_bottle_fixed_recent 
```

## Interopolate values between bottle casts to acquire 1m bins of environmental variables
```{r}

cast_bottle_fixed_recent -> test

test %>% 
  group_by(Cst_Cnt) %>% 
  nest() -> test_nest_cast

model_holder <- tibble(test_nest_cast$Cst_Cnt)
model_holder$Depthm_1mbin <- list(0)
model_holder$T_degC_1mbin <- list(0)
model_holder$Salnty_1mbin <- list(0)
model_holder$O2ml_L_1mbin <- list(0)
model_holder$O2Sat_1mbin <- list(0)

i=1

for (i in 1:nrow(model_holder)) {
model_holder$Depthm_1mbin[[i]] <- approx(test_nest_cast$data[[i]]$Depthm,test_nest_cast$data[[i]]$T_degC, method="linear", xout=seq(min(test_nest_cast$data[[i]]$Depthm),max(test_nest_cast$data[[i]]$Depthm),by=1))$x
model_holder$T_degC_1mbin[[i]] <- approx(test_nest_cast$data[[i]]$Depthm,test_nest_cast$data[[i]]$T_degC, method="linear", xout=seq(min(test_nest_cast$data[[i]]$Depthm),max(test_nest_cast$data[[i]]$Depthm),by=1))$y
model_holder$Salnty_1mbin[[i]] <- approx(test_nest_cast$data[[i]]$Depthm,test_nest_cast$data[[i]]$Salnty, method="linear", xout=seq(min(test_nest_cast$data[[i]]$Depthm),max(test_nest_cast$data[[i]]$Depthm),by=1))$y
model_holder$O2ml_L_1mbin[[i]] <- approx(test_nest_cast$data[[i]]$Depthm,test_nest_cast$data[[i]]$O2ml_L, method="linear", xout=seq(min(test_nest_cast$data[[i]]$Depthm),max(test_nest_cast$data[[i]]$Depthm),by=1))$y
model_holder$O2Sat_1mbin[[i]] <- approx(test_nest_cast$data[[i]]$Depthm,test_nest_cast$data[[i]]$O2Sat, method="linear", xout=seq(min(test_nest_cast$data[[i]]$Depthm),max(test_nest_cast$data[[i]]$Depthm),by=1))$y
}

model_holder %>% 
  pivot_longer(., cols=`Depthm_1mbin`:`O2Sat_1mbin`, values_to = "values", names_to = "metric") %>% 
  unnest(values) %>% 
  group_by(`test_nest_cast$Cst_Cnt`,metric) %>% 
  mutate(id = row_number()) %>% 
  pivot_wider(., values_from = c("values"), names_from = "metric", values_fill = NA) %>% 
  dplyr::select(Cst_Cnt=`test_nest_cast$Cst_Cnt`,Depthm_1mbin,T_degC_1mbin, Salnty_1mbin, O2ml_L_1mbin, O2Sat_1mbin) -> one_m_bin_Cst_Cnt

```

### Create Binned Data
```{r}
cast_bottle_fixed_recent %>% 
  dplyr::select(Cst_Cnt, cruise_site, Date, Year, Month, Julian_Date, Julian_Day,Lat_Dec, Lon_Dec, season,site,year_site, year_season_site, Bottom_D) %>% distinct() %>% 
  left_join(one_m_bin_Cst_Cnt) -> binned_env_data
```

### Proportion of Upper 200m That is Hypoxic
```{r}
binned_env_data %>% 
  filter(., Depthm_1mbin > 200) %>% 
  group_by(cruise_site, site, Date) %>% 
  mutate(., Hypoxic = if_else(O2Sat_1mbin <20, 1,0)) %>% 
  dplyr::summarise(Hypoxic_proportion = mean(Hypoxic)) -> Hypoxic_proportion

```

### Depth of Hypoxia O2 ml/L
```{r}
binned_env_data %>% 
  group_by(cruise_site) %>% 
  mutate(., Hypoxic = O2Sat_1mbin < 20) %>% 
  filter(., Hypoxic==TRUE ) %>% 
  group_by(cruise_site) %>% 
  slice(which.min(Depthm_1mbin)) %>% dplyr::select(cruise_site, DoH=Depthm_1mbin) -> depth_of_hypoxia
```

# Full Merge with binned environmental data
```{r}
adult_data %>% 
  mutate(., Year= as.numeric(str_sub(Date, start=1, end=4))) %>% 
  filter(., Year > 1993) %>% 
      mutate(., PA = if_else(Count_permsq2 >0,1,0)) %>% 
  left_join(binned_env_data, by="cruise_site") %>% 
  group_by(cruise_site, site=site.y, season,year_site,year_season_site, Date.x, Lat_Dec, Lon_Dec,ID_Microscopy) %>% 
  dplyr::summarise(., mean_O2_sat= mean(O2Sat_1mbin), mean_temp = mean(T_degC_1mbin), PA=mean(PA),Count_permsq2=mean(Count_permsq2)) %>% 
  mutate(., PAc=as.character(PA))-> krill_mean


```


# Focus on sites 90_35 & 86.7_45

### Map of Samples to Find the Hot Zone Site

```{r, echo=FALSE, hide=TRUE, warnings=FALSE,message=FALSE}

binned_env_data %>% 
  dplyr::select(site, Lat_Dec, Lon_Dec) %>% 
  distinct() %>% 
    filter(site %in% c("90_35", "86.7_45"))  -> to_plot

min_lat <- min(32)
max_lat <- max(35)

min_lon <- min(-121)
max_lon <- max(-117)
  
  ggplot(data = world) +
   geom_sf() +
    geom_label(data=to_plot, aes(x = Lon_Dec, y = Lat_Dec, label=site), size=2) +
    coord_sf(xlim = c(min_lon-1, max_lon+1), ylim = c(min_lat-0.5, max_lat+0.5), expand = FALSE) +theme_bw() +xlab("Longitude") +ylab("Latitude") 
  
```


### Oxygen Satuation Over Time
```{r}

binned_env_data %>% 
filter(site %in% c("90_35", "86.7_45")) %>% 
  filter(., Depthm_1mbin < 500) %>% 
  ggplot(aes(x=Date, y=Depthm_1mbin, colour=O2Sat_1mbin)) + scale_y_reverse() + geom_point() + scale_colour_cmocean( name = "oxy") +facet_wrap(site~.)
```


### Oxygen mL/L Over Time
```{r}
binned_env_data %>% 
filter(site %in% c("90_35", "86.7_45")) %>% 
    filter(., Depthm_1mbin < 500) %>% 
  ggplot(aes(x=Date, y=Depthm_1mbin, colour=O2ml_L_1mbin)) + scale_y_reverse() + geom_point() + scale_colour_cmocean( name = "oxy") +facet_wrap(site~.)

```

### Temperature Over Time
```{r}
binned_env_data %>% 
filter(site %in% c("90_35", "86.7_45")) %>% 
  filter(., T_degC_1mbin <30) %>% 
  filter(., Depthm_1mbin < 500) %>% 
  ggplot(aes(x=Date, y=Depthm_1mbin, colour=T_degC_1mbin)) + scale_y_reverse() + geom_point() + scale_colour_cmocean( name = "thermal")  +facet_wrap(site~.)


```

### Density hypoxia proportion
```{r}

Hypoxic_proportion %>% 
filter(site %in% c("90_35", "86.7_45")) %>% 
  ggplot(., aes(x=Hypoxic_proportion, color=site)) +geom_density()

```

# Krill

## Proportion of of 200m that is Hypoxic

### Krill Presence Absence Distribution Across Proportion of of 200m that is Hypoxic
```{r, fig.height=14, fig.width=12}

krill_mean %>% 
  filter(., ID_Microscopy %in% abundant_species$ID_Microscopy) %>% 
    mutate(., PA = if_else(Count_permsq2 >0,1,0)) %>% 
  mutate(., PA=as.character(PA)) %>% 
  left_join(Hypoxic_proportion) %>% 
  ggplot(aes(x=Hypoxic_proportion, color=PA,group=PA, fill=PA)) + geom_density(alpha=0.2) +facet_wrap(ID_Microscopy~.) + xlab("Proportion of Upper 200m that is Hypoxic")


```

### Krill Presences Across Average Water Column Temperature and Proportion of of 200m that is Hypoxic
```{r, fig.height=14, fig.width=12}

krill_mean %>% 
  filter(., ID_Microscopy %in% abundant_species$ID_Microscopy) %>% 
  left_join(Hypoxic_proportion) %>% 
  filter(., PAc >0) %>% 
 ggplot(aes(y=mean_temp, x=Hypoxic_proportion)) +
  stat_density_2d(aes(fill = ..level..), geom = "polygon", colour="white") +
  facet_wrap(ID_Microscopy~.) +ylab("Average Temperature Upper 210m") + 
  xlab("Proportion of Upper 200m that is Hypoxic")+theme_pubclean() + ggtitle("Presence")+theme(plot.title = element_text(size = 20, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5,size = 18, face = "bold"),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.text=element_text(size=10), 
        strip.text = element_text(size=10, face="bold"), 
        axis.title=element_text(size=16,face="bold"),
        legend.title = element_text( size=16, face="bold"),
        legend.text = element_text(size=14)
        ) 
```

### Binomial Regressons of Krill Detections As a Function of Depth of Hypoxia
```{r,fig.height=14, fig.width=12}


krill_mean %>% 
  filter(., ID_Microscopy %in% abundant_species$ID_Microscopy) %>% 
  left_join(Hypoxic_proportion) %>% 
  ggplot(aes(x=Hypoxic_proportion, y=PA)) +geom_point(alpha=0.1)+   geom_smooth(
    method="glm",
    method.args=list(family="binomial"),
  ) +
  stat_poly_eq(use_label(c("adj.R2", "p")),label.y.npc = 0.7, size=4) +  xlab("Proportion of Upper 200m that is Hypoxic") +facet_wrap(ID_Microscopy~.)


```

## Depth of Hypoxia

### Krill Presence Absence Distribution Across Depth of Hypoxia


```{r, fig.height=14, fig.width=12}

krill_mean %>% 
  filter(., ID_Microscopy %in% abundant_species$ID_Microscopy) %>% 
  mutate(., PA = if_else(Count_permsq2 >0,1,0)) %>% 
  mutate(., PA=as.character(PA)) %>% 
  left_join(depth_of_hypoxia) %>% 
  ggplot(aes(x=DoH, color=PA,group=PA, fill=PA)) + geom_density(alpha=0.2) +facet_wrap(ID_Microscopy~.)


```

### Krill Presences Across Average Water Column Temperature and Depth of Hypoxia

```{r, fig.height=14, fig.width=12}

krill_mean %>% 
  filter(., ID_Microscopy %in% abundant_species$ID_Microscopy) %>% 
  left_join(depth_of_hypoxia) %>% 
  filter(., PAc >0) %>% 
 ggplot(aes(y=mean_temp, x=DoH)) +
  stat_density_2d(aes(fill = ..level..), geom = "polygon", colour="white") +
  facet_wrap(ID_Microscopy~.) +ylab("Average Temperature Upper 210m") + 
  xlab("Depth of Hypoxia")+theme_pubclean() + ggtitle("Presence")+theme(plot.title = element_text(size = 20, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5,size = 18, face = "bold"),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.text=element_text(size=10), 
        strip.text = element_text(size=10, face="bold"), 
        axis.title=element_text(size=16,face="bold"),
        legend.title = element_text( size=16, face="bold"),
        legend.text = element_text(size=14)
        ) 
```

### Binomial Regressons of Krill Detections As a Function of Depth of Hypoxia
```{r, fig.height=14, fig.width=12}


krill_mean %>% 
  filter(., ID_Microscopy %in% abundant_species$ID_Microscopy) %>% 
  left_join(depth_of_hypoxia) %>% 
  ggplot(aes(x=DoH, y=PA)) +geom_point(alpha=0.1)+   geom_smooth(
    method="glm",
    method.args=list(family="binomial"),
  ) +
  stat_poly_eq(use_label(c("adj.R2", "p")),label.y.npc = 0.7, size=4) + xlab("Depth of Hypoxia (m)") +facet_wrap(ID_Microscopy~.)


```


## Temperature

### Krill Presence Absence Distribution Across Mean Water Column Temperature
```{r, fig.height=14, fig.width=12}

krill_mean %>% 
  filter(., ID_Microscopy %in% abundant_species$ID_Microscopy) %>% 
    mutate(., PA = if_else(Count_permsq2 >0,1,0)) %>% 
  mutate(., PA=as.character(PA)) %>% 
  left_join(Hypoxic_proportion) %>% 
  ggplot(aes(x=mean_temp, color=PA,group=PA, fill=PA)) + geom_density(alpha=0.2) +facet_wrap(ID_Microscopy~., scales="free_y") + xlab("Average Water Column Temperature ˚C")


```

### Krill Presences Across Average Water Column Temperature and O2 Saturation
```{r, fig.height=14, fig.width=12}

krill_mean %>% 
  filter(., ID_Microscopy %in% abundant_species$ID_Microscopy) %>% 
  left_join(Hypoxic_proportion) %>% 
  filter(., PAc >0) %>% 
 ggplot(aes(y=mean_temp, x=mean_O2_sat)) +
  stat_density_2d(aes(fill = ..level..), geom = "polygon", colour="white") +
  facet_wrap(ID_Microscopy~.) +ylab("Average Temperature Upper 210m") + 
  xlab("Average O2 Sat. Upper 210m")+theme_pubclean() + ggtitle("Presence")+theme(plot.title = element_text(size = 20, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5,size = 18, face = "bold"),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.text=element_text(size=10), 
        strip.text = element_text(size=10, face="bold"), 
        axis.title=element_text(size=16,face="bold"),
        legend.title = element_text( size=16, face="bold"),
        legend.text = element_text(size=14)
        ) 
```

### Binomial Regressons of Krill Detections As a Function of Depth of Hypoxia
```{r, fig.height=14, fig.width=12}


krill_mean %>% 
  filter(., ID_Microscopy %in% abundant_species$ID_Microscopy) %>% 
  ggplot(aes(x=mean_temp, y=PA)) +geom_point(alpha=0.1)+   geom_smooth(
    method="glm",
    method.args=list(family="binomial"),
  ) +
  stat_poly_eq(use_label(c("adj.R2", "p")),label.y.npc = 0.7, size=4) +  xlab("Average Temperature Upper 210m") +facet_wrap(ID_Microscopy~.)


```



