---
title: "Denoising and decontaminating v2"
output: html_notebook
date: 6-22-2020
Author: Zack Gold
contributions from: Ramon Gallego & Ryan Kelly
---


# Load the dataset and metadata

```{r load libraries, include=FALSE}
 knitr::opts_chunk$set(warning = FALSE)

library (tidyverse)
library (vegan)
library (proxy)
library(reshape2)
library(microDecon)
library(stringr)
```

#### Functions
Need to Build out this section to make a universal decontamination package. Punting for now.
```{r How.many}
#Function Name: How many function
#Use: To calculate number of hashes (ASVs), number of reads, and number of samples at ech stage of the decontamination pipeline
how.many <- function(ASVtable, round){
  ASVtable %>% ungroup() %>% 
    dplyr::summarise(nsamples = n_distinct(sample),
              nHashes = n_distinct(Hash),
              nReads = sum(nReads), 
              Stage = paste0("Step_", round)) %>% 
    gather(starts_with("n"), value = "number", key = "Stat")
}

#Function Name: load_anacapa_edited
#Use: Import Anacapa output file
load_anacapa_edited <- function(data_path){
  read.table(data_path, header = 1, sep = "\t", stringsAsFactors = F)
}
```

We will load the metadata and Hash.Key files.
#Load Data
```{r load metadata datasets - we will be doing that for all runs}
#Set Working Directory
setwd("/Users/zackgold/Documents/UCLA_phd/Projects/California/NOAA_CALCOFI/data_an_2020/analysis_062020")

#Metadata Upload
input_meta_path <- "/Users/zackgold/Documents/UCLA_phd/Projects/California/NOAA_CALCOFI/CalCOFI_Database_194903-201806_csv_12Jun2019/calcofi_metadata_edited_06222020.txt"

metadata <- read.table(input_meta_path, header = 1, sep = "\t", stringsAsFactors = F)

metadata %>% 
unite(., col = sample2, c("Location", "ext_rep","tech_rep"), remove = FALSE) %>% #needed for matching to ASV Table
  mutate( sample_new = if_else(is.na(Location), sample,sample2)) ->metadata

#Hash.Key Upload
input_hash_path <- "/Users/zackgold/Documents/UCLA_phd/Projects/California/NOAA_CALCOFI/data_an_2020/analysis_062020/Hashes_06222020.txt"

Hash.key <- read.table(input_hash_path, header = 1, sep = "\t", stringsAsFactors = F)

input_hash_uniter_path <- "/Users/zackgold/Documents/UCLA_phd/Projects/California/NOAA_CALCOFI/data_an_2020/analysis_062020/hashuniter.txt"

```

```{r}
#Import NextSeq Data
calcofi_nextseq <- load_anacapa_edited("/Users/zackgold/Documents/UCLA_phd/Projects/California/NOAA_CALCOFI/data_an_2020/analysis_062020/nextseq_fishcard_12S_all_taxonomy_tables/Summary_by_percent_confidence/60/nextseq_fishcard_12S_all_ASV_raw_taxonomy_60_edited.txt")
calcofi_nextseq$Miseq_run <- "nextseq"

#Transform NextSeq Sample Names
calcofi_nextseq_names <- colnames(calcofi_nextseq)
calcofi_nextseq_names %>% as.data.frame() -> calcofi_nextseq_names
colnames(calcofi_nextseq_names) <- c("sample")
calcofi_nextseq_names %>% 
  mutate(sample =str_replace(sample, ".L001", "") ) %>% 
  left_join(metadata) %>% 
  unite(., col = sample2, c("Location", "ext_rep","tech_rep"), remove = FALSE) %>% 
  mutate( sample_new = if_else(is.na(Location), sample,sample2)) %>% 
  dplyr::select(sample, sample_new) -> calcofi_nextseq_names
colnames(calcofi_nextseq) <- calcofi_nextseq_names$sample_new

#Check NextSeq Data
colnames(calcofi_nextseq)
head(calcofi_nextseq)
dim(calcofi_nextseq)
```

```{r}
#Import Seb Data
calcofi_seb <- load_anacapa_edited("/Users/zackgold/Documents/UCLA_phd/Projects/California/NOAA_CALCOFI/data_an_2020/analysis_062020/Min_sebastes_ASV_raw_taxonomy_40_annotated_min_edited.txt")
calcofi_seb$Miseq_run <- "seb"

#Transform Seb Names
calcofi_seb_names <- colnames(calcofi_seb)
calcofi_seb_names %>% as.data.frame() -> calcofi_seb_names
colnames(calcofi_seb_names) <- c("sample")
calcofi_seb_names %>% 
  left_join(metadata) %>% 
  unite(., col = sample2, c("Location", "ext_rep","tech_rep"), remove = FALSE) %>% 
  mutate( sample_new = if_else(is.na(Location), sample,sample2)) %>% 
  dplyr::select(sample, sample_new) -> calcofi_seb_names
colnames(calcofi_seb) <- calcofi_seb_names$sample_new

#Check Seb Names
colnames(calcofi_seb)
head(calcofi_seb)
dim(calcofi_seb)
```

#Transform Data
```{r}
#Merge All Tables
ASV.table <- bind_rows(calcofi_nextseq,
                       calcofi_seb)

#Replace NAs that arise from different controls (Seb had no reads recorded in blanks)
ASV.table %>% 
  replace(is.na(.), 0) ->ASV.table

#Check Merge
dim(ASV.table)
head(ASV.table)
tail(ASV.table)

#Convert to Long Data Format
ASV.table$seq_number <- factor(ASV.table$seq_number)
ASV.table$Miseq_run <- factor(ASV.table$Miseq_run)

columns <- colnames(ASV.table)
remove <- c("seq_number","sum.taxonomy","Miseq_run")

gathercols <-  columns[! columns %in% remove] 

ASV.table <- gather(ASV.table, sample, reads, gathercols, factor_key=TRUE)
ASV.table$reads <- as.numeric(ASV.table$reads)

```

# Cleaning Process 0: ** Remove all Forward, Reverse, and Unmerged reads**
```{r}
#Filter Merged only reads
ASV.table %>% 
  filter(., str_detect(seq_number,"merged")) %>% 
    filter(., !str_detect(seq_number,"unmerged")) -> ASV.table_merged

#Calculate % ASVs Kept
ASV.table %>%  dim() -> all_dim
ASV.table_merged %>%  dim() -> merged_only_dim

merged_only_dim[[1]]/all_dim[[1]]*100
#0.65% of ASVs retained....

#Save Merged ASV Table since the above loading steps are time intensive
saveRDS(ASV.table_merged,file="ASV.table_merged") 
readRDS(file="ASV.table_merged") -> ASV.table_merged
```

Final outputs of Step 0 are a clean ASV meged reads only table, clean metadata file, and a Hash.Key file.

# Cleaning Process 1: **Estimation of *Tag-jumping* or sample *cross-talk* **

The objective of this step is to see how many sequences from the positives controls appeared in the environmental samples vice versa.

```{r split into positives and samples}

#Create list of control samples
metadata %>% 
  filter(Sample_Control=="Control") %>% 
  dplyr::select(sample_new) %>% unique() -> controls
controls <- controls$sample_new

#Create List of Positive Controls
metadata %>% 
  filter(Control_type=="Pos") %>% 
  dplyr::select(sample_new) %>% unique()-> pos_controls
pos_controls <- pos_controls$sample_new

#Create List of Negative Controls
metadata %>% 
  filter(Control_type=="Neg") %>% 
  dplyr::select(sample_new) %>% unique() -> neg_controls
neg_controls <- neg_controls$sample_new

#New column that labels each ASV as originiating in Positive controls, negative controls, or env. samples
ASV.table_merged %>% 
  mutate(source = case_when(sample %in% pos_controls~"Positives",
                            sample %in% neg_controls~"Blanks",
                             TRUE ~"Samples")) -> ASV.table_merged

#Convert to tibble
ASV.table_merged <- as_tibble(ASV.table_merged)

#Remove empty sequences
ASV.table_merged %>% 
  filter(reads != 0)  -> ASV.table_merged

#Rename Columns and remove seq_number
ASV.table_merged %>%
  mutate(Hash = as.character(seq_number),
         sample = as.character(sample),
         nReads = reads)   -> ASV.table_merged

#Create a List of ASVs that were in controls
ASV.table_merged %>% 
  filter (source %in% c("Positives","Blanks")) %>%
  dplyr::group_by(Hash) %>% 
  dplyr::summarise(tot = sum(reads)) %>% 
  arrange(desc(tot)) %>% 
  pull(Hash) -> all.seqs.in.ctrls

#Explore potential contamination
ASV.table_merged %>% 
  as.data.frame() %>% 
  filter (source %in% c("Positives","Blanks")) %>%
  dplyr::group_by(Hash,sample) %>% 
  dplyr::summarise(tot = sum(reads)) %>% 
  arrange(desc(tot)) %>% 
  dplyr::select(Hash,tot,sample) %>% 
  left_join(Hash.key, by=c("Hash"="seq_number")) %>%  View()

#Create list of contaminant species
Hash.key %>% 
  filter(seq_number %in% all.seqs.in.ctrls) %>% as.tibble() -> contam.species

contam.species$sum.taxonomy %>%  unique()
```

Visualize Contamination through Sequencing Depth Plots
```{r}
#NextSeq Sequence Depth Plot
ASV.table_merged %>% 
  group_by(sample) %>%
  filter(., Miseq_run=="nextseq") %>% 
  mutate (TotalReadsperSample = sum(nReads)) %>%
  arrange(desc(TotalReadsperSample)) %>%
  ggplot(., aes(x=sample, y=TotalReadsperSample, color=source)) + geom_point() +ggtitle("Read Count Across Samples") + theme(axis.text.x = element_text(angle = 90)) +
  scale_y_continuous(trans='log10')

#Check contamination in blanks
ASV.table_merged %>% 
  group_by(sample) %>%
  filter(., Miseq_run=="nextseq") %>%
  filter(., sample %in% neg_controls) %>% 
  group_by(sum.taxonomy) %>% 
  summarise( tot_reads=sum(nReads))

#High levels of anchovy in negative controls.

```

```{r}
#Sebastes Sequencing Depth Plot
ASV.table_merged %>% 
  group_by(sample) %>%
  filter(., Miseq_run=="seb") %>% 
  mutate (TotalReadsperSample = sum(nReads)) %>%
  arrange(desc(TotalReadsperSample)) %>%
  ggplot(., aes(x=sample, y=TotalReadsperSample, color=source)) + geom_point() +ggtitle("Read Count Across Samples") + theme(axis.text.x = element_text(angle = 90)) +
  scale_y_continuous(trans='log10')

#Check contamination in blanks
ASV.table_merged %>% 
  group_by(sample) %>%
  filter(., Miseq_run=="seb") %>%
  filter(., sample %in% neg_controls) %>% 
  group_by(sum.taxonomy) %>% 
  summarise( tot_reads=sum(nReads))
#Literally no contamination

```


### Step 1: Nest the dataset and split it in positives and samples

```{r nesting the dataset}
#Nest the Dataset
ASV.table_merged %>% 
  dplyr::group_by(Miseq_run, source) %>% 
  nest() %>% 
  pivot_wider(names_from=source, values_from=data) -> ASV.nested
```

```{r summary.file}
#Create Summary Table of results to document effects of each decontamination step
ASV.nested %>% 
  ungroup() %>% 
  dplyr::transmute(.,Miseq_run,Summary = purrr::map(Samples, ~ how.many(ASVtable = ., round = 0)))  -> ASV.summary

ASV.summary$Summary
#Elas had some samples in which all reads were removed
```


### Step 2: Model the composition of the positive controls of each run 

```{r jumping vector}

ASV.nested %>% 
  mutate (contam.tibble = purrr::map(Positives, 
                              function(.x){
                                .x %>%
                                  ungroup() %>% 
                                  group_by(sample) %>%
                                  mutate (TotalReadsperSample = sum(nReads)) %>%
                                  mutate (proportion = nReads/TotalReadsperSample) %>%
                                  group_by(Hash) %>%
                                  dplyr::summarise (vector_contamination = max(proportion))
                                }) ) -> ASV.nested

ASV.nested$contam.tibble[[1]] %>% as.data.frame() %>% 
  ggplot(aes(x= vector_contamination))+
  geom_histogram()# Check how it looks like

ASV.nested$contam.tibble[[2]] %>% as.data.frame() %>% 
  ggplot(aes(x= vector_contamination))+
  geom_histogram()# Check how it looks like
```

### Step 3: Substract the composition of the positive controls from the environment samples

The idea behind this procedure is that we know, for each run, how many reads from each Hash appeared in teh positive controls. These come from 2 processes: sequences we know should appear in the positive controls, and sequences that have *jumped* from the environment to the positive controls. With this procedure, we substract from every environmental sample the proportion of reads that jumped from elsewhere.

```{r cleaning step 1}
ASV.nested %>% 
  ungroup() %>% 
  mutate(cleaned.tibble = map2(Samples, contam.tibble, function(.x,.y){ 
    .x %>%
      dplyr::group_by (sample) %>%
      mutate (TotalReadsperSample = sum (nReads)) %>%
      left_join(.y, by = "Hash") %>%
      mutate (Updated_nReads = ifelse (!is.na(vector_contamination),  nReads - (ceiling(vector_contamination*TotalReadsperSample)), nReads)) %>%
      filter (Updated_nReads > 0) %>%
      ungroup() %>% 
      dplyr::select (sample, Hash, nReads = Updated_nReads)
  })) -> ASV.nested


ASV.nested$cleaned.tibble[[1]] %>% as.data.frame() %>% 
  arrange(desc(nReads)) %>% head(n=100) #Check how they look

ASV.nested$cleaned.tibble[[2]] %>% as.data.frame() %>% 
  arrange(desc(nReads)) %>% head(n=100) #Check how they look


```

```{r summary.file.2}
#Visualize Effects of Cleaning Process 1
ASV.nested %>% 
  ungroup() %>%
  transmute(Miseq_run, Summary.1 = purrr::map(cleaned.tibble, ~ how.many(ASVtable = .,round = "1.Jump"))) %>% 
  left_join(ASV.summary) %>% #use left join when there are many miseq runs to join
  mutate(Summary= map2(Summary, Summary.1, bind_rows)) %>%
  dplyr::select(-Summary.1) -> ASV.summary 

ASV.summary$Summary
```


# Cleaning Process 2: **Discarding PCR replicates with low number of reads**

We will fit the number of reads assigned to each sample to a normal distribution and discard those samples with a probability of 95% of not fitting in that distribution. The output would be a dataset with less samples and potentially less number of unique Hashes.


```{r fitting nReads per sample}

#Calculate Read Depth for Each Sample
ASV.nested %>% 
  select(Miseq_run,cleaned.tibble) %>% 
  unnest(cleaned.tibble) %>%
  group_by(Miseq_run,sample) %>%
  dplyr::summarise(tot = sum(nReads)) %>% 
  arrange(desc(tot))-> all.reps

#Visualize Read Depth in groups
all.reps %>%
  ungroup() %>% 
  mutate(., to_keep = case_when(tot > 100000 ~ ">100K",
                                tot > 75000 ~ ">75K",
                                tot > 50000 ~ ">50K",
                                tot > 25000 ~ ">25K",
                                tot > 10000 ~ ">10K",
                                TRUE ~ "TRASH")) %>% 
  count(to_keep) %>% 
  mutate(., total=sum(n)) %>% 
  mutate(per=paste0(round(100*n/total,2),'%')) %>% 
  dplyr::select(-total)

#Histogram of Read Depth
all.reps %>% ggplot(., aes(x=tot)) + geom_histogram()

```

```{r}

#Fit Normal Distribution to reads ***
#**** Read distributions rarely fit a normal distribution. They tend to be highly right skewed. We don't particularly care if some samples have too many reads, it is more important to remove low level reads. Calculating a beta dist. is actually quite difficult as starting values for the model fitting are needed. Potentially a better solution maybe to exclude right skewed outliers and recalculate.

all.reps %>%
  pull(tot) -> reads.per.sample
  
names(reads.per.sample) <-  all.reps %>%  pull(sample)  

normparams.reads <- MASS::fitdistr(reads.per.sample, "normal")$estimate

all.reps%>%
  mutate(prob = pnorm(tot, normparams.reads[1], normparams.reads[2])) -> all.reps
next.reps %>% View()

#Filter reads based on probability distribution as well as read depth cut off
outliers <- all.reps %>% 
  filter(prob < 0.05 | tot < 30000)

#Cut off is 30K reads, potentially need to be more conservative.

#Filter Next Seq Data
outliers %>%  filter(., Miseq_run=="nextseq") -> nextseq_outliers

ASV.nested$cleaned.tibble[[1]] %>% 
   filter(.,!sample %in% nextseq_outliers$sample) -> nextseq.step1.low.reads

#Filter Seb Data
outliers %>%  filter(., Miseq_run=="seb") -> seb_outliers

ASV.nested$cleaned.tibble[[2]] %>% 
   filter(.,!sample %in% seb_outliers$sample) -> seb.step1.low.reads

#Reconstruct new ASV nested step
ASV.nested %>% 
  mutate(Step.1.low.reads = list(
                             nextseq.step1.low.reads,
                             seb.step1.low.reads)) -> ASV.nested

#Visualize Results of Cleaning Step 2
ASV.nested %>% 
  transmute(Miseq_run, Summary.1 = purrr::map(Step.1.low.reads, ~ how.many(ASVtable = .,round = "2.Low.nReads"))) %>% 
  left_join(ASV.summary) %>% 
  mutate(Summary   = map2(Summary, Summary.1, bind_rows)) %>%
  dplyr::select(-Summary.1) -> ASV.summary 

ASV.summary$Summary
```

# Cleaning Process 3: **Full clearance from Negative control influence**
We will follow microDecon here

#####MicroDecon NextSeq
```{r cleaning.Step2}
ASV.nested$Blanks[[1]] %>% 
  select(sample,Hash, nReads) -> blankers

ASV.nested$Step.1.low.reads[[1]] %>% 
  arrange(sample) -> nextseq_long


rbind(blankers, nextseq_long) -> step.1.1

step.1.1 %>% 
pivot_wider(names_from=sample, values_from=nReads, values_fill = list(nReads =0)) -> step.1.1_wide

step.1.1_wide %>%
  mutate(seq_number=Hash) %>% 
  left_join(Hash.key) %>%
  select(-seq_number) -> step.1.1_wide

as.data.frame(step.1.1_wide) -> step.1.1_wide
#step.1.1_wide %>% View()

ASV.nested$Blanks[[1]]$sample %>% unique() %>% length() -> blank_num
ASV.nested$Step.1.low.reads[[1]]$sample %>% unique() %>% length() -> sample_num

ASV.nested$Blanks[[1]]$sample %>% unique() -> blank_samples

append(blank_samples, c("sum.taxonomy","Hash")) -> col_delete
colnames(step.1.1_wide) %>%  as.data.frame() %>% 
  filter(., !(. %in% col_delete)) %>% 
  mutate(., sample2=.) %>% 
  left_join(metadata) %>% 
  filter(., Barcode!="Sebastes") %>% dplyr::select(sample2,Location,ext_rep) %>% 
  group_by(Location,ext_rep) %>% 
  count() -> sample_counter
sample_counter$n

#rep(3, times = (sample_num/3))
step.1.1_decon_nextseq <- decon(data=step.1.1_wide, numb.blanks = blank_num, numb.ind=sample_counter$n
, taxa = T, prop.thresh = 5e-05)


#step.1.1_decon_elas_a$reads.removed %>% View()

step.1.1_decon_nextseq$decon.table

columns <- colnames(step.1.1_decon_nextseq$decon.table)
remove <- c("Hash","sum.taxonomy")

gathercols <-  columns[! columns %in% remove] 

# Convert to Long Data
step.1.1_decon_nextseq_clean <- gather(step.1.1_decon_nextseq$decon.table, sample, nReads, gathercols, factor_key=TRUE)

step.1.1_decon_nextseq_clean %>% as.tibble() %>% 
  select(-sum.taxonomy) %>% 
  filter(., sample != "Mean.blank") %>% 
  filter(., nReads >0) -> step.1.1_decon_nextseq_clean_tibble

#A lot of Anchovy reads were removed, although not all
step.1.1_decon_nextseq_clean_tibble %>% 
  left_join(Hash.key, by=c("Hash"="seq_number")) %>% 
  filter(., sum.taxonomy=="Eukaryota;Chordata;Actinopteri;Clupeiformes;Engraulidae;Engraulis;Engraulis mordax")

step.1.1_decon_nextseq$reads.removed %>% 
  filter(., sum.taxonomy=="Eukaryota;Chordata;Actinopteri;Clupeiformes;Engraulidae;Engraulis;Engraulis mordax")
```

#####MicroDecon Seb
Not executed because no merged reads entered a single blank. Nice to have a genus specific barcode!


```{r Save Files Before Occupancy}
#Recombine Data
ASV.nested %>% 
  mutate(Step2.tibble = list(
                             step.1.1_decon_nextseq_clean_tibble,
                             ASV.nested$Step.1.low.reads[[2]])) -> ASV.nested


#Visualize Results of Cleaning Process 3
ASV.nested %>% 
  transmute(Miseq_run, Summary.1 = purrr::map(Step2.tibble, ~ how.many(ASVtable = .,round = "3.Positives"))) %>%
  left_join(ASV.summary) %>% 
  mutate(Summary = map2(Summary, Summary.1, bind_rows)) %>%
  dplyr::select(-Summary.1) -> ASV.summary

ASV.summary$Summary


#Save Files Before Occupancy
saveRDS(ASV.nested, file = "Cleaning.before.Occ.model")
saveRDS(ASV.summary, file = "ASV.summary.rds")


```

```{r}
ASV.summary <- readRDS(file ="ASV.summary.rds")

ASV.nested <- readRDS(file ="Cleaning.before.Occ.model")

```

```{r output file before occupancy}

ASV.nested %>% 
  unnest(Step2.tibble) %>%
  as.data.frame() %>% 
  filter(., nReads>1) %>% 
  mutate(.,seq_number=Hash) %>%  
  left_join(Hash.key) %>% 
  dplyr::group_by(sum.taxonomy, sample) %>% 
  dplyr::summarise(., total_reads = sum(nReads)) %>% #sum by taxonomy per site
  spread(., key = "sample", value = "total_reads", fill = 0) -> preoccupancy_sum.taxonomy

saveRDS(preoccupancy_sum.taxonomy, file = "preoccupancy.sum.taxonomy.rds")
write_csv(preoccupancy_sum.taxonomy ,"sum_taxonomy_pre_occupancy_both.csv")

bind_rows(ASV.nested$Step2.tibble[[1]],ASV.nested$Step2.tibble[[2]]) %>% 
  as.data.frame() %>% 
  mutate(.,seq_number=Hash) %>%  
  left_join(Hash.key) %>%
  spread(., key = "sample", value = "nReads", fill = 0) %>% dplyr::select(-seq_number) -> ASV_pre_occ

saveRDS(ASV_pre_occ, file = "ASV_pre_occupancy.rds")
write_csv(ASV_pre_occ ,"ASV_pre_occupancy.csv")

```

At this point the SOM is a separate script. Please see SOM_calcofi06242020.R for the actual site occupancy modeling.

# Cleaning Process 4: **Occupancy modelling**
```{r importing Occ results}

calcofi_occupancy_results_all <- readRDS(file="calcofi_occupancy_results_all.RDS")
calcofi_occupancy_results_9 <- readRDS(file="calcofi_occupancy_results_9.RDS")

ASV.nested <- readRDS(file ="Cleaning.before.Occ.model")
ASV.summary <- readRDS(file ="ASV.summary.rds")

```

```{r Visualize SOM}
#View Histogram
calcofi_occupancy_results_all %>% 
  pull(max_Occupancy_prob) %>% 
  hist()

```

So we will throw away most of the Hashes, but will keep most of the reads - we are getting into something here

```{r actual filtering}

#Filter Species that did not pass SOM
ASV.nested %>% 
  mutate (Step2.tibble.edited = purrr::map(Step2.tibble, 
                              function(.x){
                                .x %>%
                                mutate(., seq_number=Hash) %>%
                                left_join(Hash.key)
                                }) ) -> ASV.nested

ASV.nested %>% 
mutate(Step3.tibble.9 = purrr::map (Step2.tibble.edited, ~ filter(.,sum.taxonomy %in% calcofi_occupancy_results_9$sum.taxonomy) %>% ungroup))-> ASV.nested

#Visualize Results of Clearence Process 4
ASV.nested %>% 
  transmute(Miseq_run, Summary.1 = purrr::map(Step3.tibble.9, ~ how.many(ASVtable = .,round ="4.Occupancy.9"))) %>% 
  left_join(ASV.summary) %>%
  mutate(Summary   = map2(Summary, Summary.1, bind_rows)) %>%
  dplyr::select(-Summary.1) -> ASV.summary

ASV.summary$Summary
#Discarded the vast majority of ASVs, but retained most of the reads
```

```{r}

#Save Data
saveRDS(ASV.nested,file="ASV.nested_post_occ.RDS")
saveRDS(ASV.summary,file="ASV.summary_post_occ.RDS")

#Reupload Data
ASV.nested <- readRDS(file ="ASV.nested_post_occ.RDS")
ASV.summary <- readRDS(file ="ASV.summary_post_occ.RDS")

#Explore Summary of Each Sequence Run
ASV.summary %>% 
  dplyr::select(Miseq_run,Summary) %>% 
  unnest(Summary) %>% 
  separate(Miseq_run, c("barcode","rep")) %>% 
  group_by(barcode,Stage,Stat) %>% 
  summarise(sum =sum(number))

#Explore Total Date
ASV.summary %>% 
  dplyr::select(Miseq_run,Summary) %>% 
  unnest(Summary) %>% 
  group_by(Stage,Stat) %>% 
  summarise(sum =sum(number))

```
So we will throw away most of the Hashes, but will keep most of the reads - we are getting into something here

# Cleaning Process 5: **Dissimilarity between PCR (technical) replicates**
```{r dissimilarity between PCR replicates}
metadata$sample2
ASV.nested %>% 
  dplyr::select(Miseq_run,Step3.tibble.9) %>% 
  unnest(Step3.tibble.9) %>% 
  ungroup() %>% 
  unite(sample_unique, c("Miseq_run","sample"),sep=":",remove=FALSE) %>% 
  dplyr::group_by(sum.taxonomy,sample_unique) %>%
  dplyr::summarise(nReads=sum(nReads)) %>% 
  separate(sample_unique, c("Miseq_run","sample"),sep=":",remove=TRUE) %>% 
  mutate(., Barcode = case_when(Miseq_run == "nextseq"~"MiFish",
                                Miseq_run == "seb"~"Sebastes")) %>%
  left_join(metadata, by=c("Barcode","sample"="sample2")) %>% 
  unite(sample_unique, c("Barcode","sample"),sep=":",remove=FALSE)   -> cleaned.tibble.post_occ.9

ASV.nested %>% 
  dplyr::select(Miseq_run,Step2.tibble) %>% 
  unnest(Step2.tibble) %>% 
  ungroup() %>% 
  mutate(seq_number=Hash) %>% 
  left_join(Hash.key, by="seq_number") %>% 
  unite(sample_unique, c("Miseq_run","sample"),sep=":",remove=FALSE) %>% 
  dplyr::group_by(sum.taxonomy,sample_unique) %>%
  dplyr::summarise(nReads=sum(nReads)) %>% 
  separate(sample_unique, c("Miseq_run","sample"),sep=":",remove=TRUE)  %>% 
  mutate(., Barcode = case_when(Miseq_run == "nextseq"~"MiFish",
                                Miseq_run == "seb"~"Sebastes")) %>%
  left_join(metadata, by=c("Barcode","sample"="sample2"))%>% 
  unite(sample_unique, c("Barcode","sample"),sep=":",remove=FALSE)-> cleaned.tibble.pre_occ

```

```{r quick check}


cleaned.tibble.post_occ.9 %>%
  ungroup() %>% 
  dplyr::summarise(n_distinct(sample_unique), #537
            n_distinct(sum.taxonomy))  #135

cleaned.tibble.pre_occ %>% 
  ungroup() %>% 
  dplyr::summarise(n_distinct(sample_unique), # 537
            n_distinct(sum.taxonomy)) #159

# Let's check the levels of replication

cleaned.tibble.post_occ.9 %>% 
  group_by(Miseq_run,Location,ext_rep) %>% 
  dplyr::summarise(nrep = n_distinct(tech_rep)) %>%
  filter (nrep == 3) #172
  #filter (nrep == 2) # 9
  #filter (nrep == 1) # 

cleaned.tibble.pre_occ %>% 
  group_by(Miseq_run,Location,ext_rep) %>% 
  dplyr::summarise(nrep = n_distinct(tech_rep)) %>%
  filter (nrep == 3) #172
  #filter (nrep == 2) # 9
  #filter (nrep == 1) # 

```

```{r lets do the PCR replication}
cleaned.tibble.post_occ.9 %>%
  ungroup() %>% 
  dplyr::group_by(sample_unique) %>%
  mutate (Tot = sum(nReads),
          Row.sums = nReads / Tot) %>% 
  dplyr::group_by (sum.taxonomy) %>%
  mutate (Colmax = max (Row.sums),
          Normalized.reads = Row.sums / Colmax) -> cleaned.tibble.post_occ.9 #transforms raw number of reads to eDNA index

cleaned.tibble.pre_occ %>%
    ungroup() %>% 
  dplyr::group_by (sample_unique) %>%
  mutate (Tot = sum(nReads),
          Row.sums = nReads / Tot) %>% 
  dplyr::group_by (sum.taxonomy) %>%
  mutate (Colmax = max (Row.sums),
          Normalized.reads = Row.sums / Colmax) -> cleaned.tibble.pre_occ #transforms raw number of reads to eDNA index


tibble_to_matrix <- function (tb) {
  tb %>% 
    group_by(sample_unique, sum.taxonomy) %>% 
    dplyr::summarise(nReads = sum(Normalized.reads)) %>% 
    spread ( key = "sum.taxonomy", value = "nReads", fill = 0) %>% 
      ungroup() -> matrix_1
    samples <- pull (matrix_1, sample_unique)
    matrix_1[,-1] -> matrix_1
    data.matrix(matrix_1) -> matrix_1
    dimnames(matrix_1)[[1]] <- samples
    vegdist(matrix_1) -> matrix_1
}
tibble_to_matrix (cleaned.tibble.post_occ.9) -> all.distances.full.post.9

tibble_to_matrix (cleaned.tibble.pre_occ) -> all.distances.full.pre


#names(all.distances.full)


summary(is.na(names(all.distances.full.post.9)))
summary(is.na(names(all.distances.full.pre)))

```

```{r}
as.tibble(subset(melt(as.matrix(all.distances.full.post.9)))) -> all.distances.melted.post.9
as.tibble(subset(melt(as.matrix(all.distances.full.pre)))) -> all.distances.melted.pre

summary(is.na(all.distances.melted.post.9$value))
summary(is.na(all.distances.melted.pre$value))

```

```{r}
# Now, create a three variables for all distances, they could be PCR replicates, BIOL replicates, or from the same site

all.distances.melted.pre %>% 
  separate(., Var1, into = c("barcode1","sample1"), sep=":") %>% 
  left_join(metadata,by=c("barcode1"="Barcode","sample1"="sample2"))%>% 
  dplyr::select(barcode1,sample1,location1=ST_ID,Year1=Year,ext_rep1=ext_rep,tech_rep1=tech_rep,Var2,value) %>% 
  separate(., Var2, into = c("barcode2","sample2"), sep=":") %>% 
  left_join(metadata,by=c("barcode2"="Barcode","sample2"))%>% 
  dplyr::select(barcode1,sample1,location1,Year1,ext_rep1,tech_rep1,barcode2,sample2,location2=ST_ID,Year2=Year,ext_rep2=ext_rep,tech_rep2=tech_rep,value) %>% 
  unite(location1,Year1, col= "station1", remove=F) %>% 
  unite( location2,Year2, col= "station2", remove=F) %>% 
  unite( barcode1,station1,ext_rep1, col= "tech1", remove=F) %>% 
  unite( barcode2,station2,ext_rep2, col= "tech2", remove=F) %>% 
  unite( barcode1,station1, col= "ext1", remove=F) %>% 
  unite( barcode2,station2, col= "ext2", remove=F) %>% 
  unite( barcode1,Year1, col= "year1", remove=F) %>% 
  unite( barcode2,Year2, col= "year2", remove=F) %>% 
  unite( barcode1,location1, col= "location1", remove=F) %>% 
  unite( barcode2,location2, col= "location2", remove=F) %>% 
  unite( barcode1,station1,tech_rep1, col= "Sample1", remove=F) %>% 
  unite( barcode2,station2, tech_rep2,, col= "Sample2", remove=F) %>% 
  mutate(Distance.type = case_when(tech1 == tech2 ~ "PCR.replicates",
                                   ext1 == ext2 ~ "Jar.rep",
                                   year1 == year2 ~ "Same Barcode Same Year",
                                  barcode1 == barcode2 ~ "Same Barcode Different Site",
                                      TRUE ~ "Different Barcode Different Site"
                                     )) %>% 
  dplyr::select(Sample1, Sample2, value , Distance.type) %>%
  filter(Sample1 != Sample2) -> all.distances.to.plot.pre

# Checking all went well
sapply(all.distances.to.plot.pre, function(x) summary(is.na(x)))

all.distances.to.plot.pre$Distance.type <- all.distances.to.plot.pre$Distance.type  %>% fct_relevel( "PCR.replicates", "Jar.rep", "Same Barcode Same Year","Same Barcode Different Site","Different Barcode Different Site")

  ggplot (all.distances.to.plot.pre , aes (fill = Distance.type, x = value,after_stat(density))) +
  geom_histogram(stat = 'bin', alpha = 0.9, binwidth = 0.01) + #xlim(0, 1) +
  facet_wrap( ~ Distance.type) +
 labs (x = "Pairwise Dissimilarity", y = "Density" ,
        fill = "Groups", title = "eDNA Pairwise Dissimilarity Pre Occ") +theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank())
  
```


```{r}
# Now, create a three variables for all distances, they could be PCR replicates, BIOL replicates, or from the same site

all.distances.melted.post.9 %>% 
  separate(., Var1, into = c("barcode1","sample1"), sep=":") %>% 
  left_join(metadata,by=c("barcode1"="Barcode","sample1"="sample2"))%>% 
  dplyr::select(barcode1,sample1,location1=ST_ID,Year1=Year,ext_rep1=ext_rep,tech_rep1=tech_rep,Var2,value) %>% 
  separate(., Var2, into = c("barcode2","sample2"), sep=":") %>% 
  left_join(metadata,by=c("barcode2"="Barcode","sample2"))%>% 
  dplyr::select(barcode1,sample1,location1,Year1,ext_rep1,tech_rep1,barcode2,sample2,location2=ST_ID,Year2=Year,ext_rep2=ext_rep,tech_rep2=tech_rep,value) %>% 
  unite(location1,Year1, col= "station1", remove=F) %>% 
  unite( location2,Year2, col= "station2", remove=F) %>% 
  unite( barcode1,station1,ext_rep1, col= "tech1", remove=F) %>% 
  unite( barcode2,station2,ext_rep2, col= "tech2", remove=F) %>% 
  unite( barcode1,station1, col= "ext1", remove=F) %>% 
  unite( barcode2,station2, col= "ext2", remove=F) %>% 
  unite( barcode1,Year1, col= "year1", remove=F) %>% 
  unite( barcode2,Year2, col= "year2", remove=F) %>% 
  unite( barcode1,location1, col= "location1", remove=F) %>% 
  unite( barcode2,location2, col= "location2", remove=F) %>% 
  unite( barcode1,station1,tech_rep1, col= "Sample1", remove=F) %>% 
  unite( barcode2,station2, tech_rep2,, col= "Sample2", remove=F) %>% 
  mutate(Distance.type = case_when(tech1 == tech2 ~ "PCR.replicates",
                                   ext1 == ext2 ~ "Jar.rep",
                                   year1 == year2 ~ "Same Barcode Same Year",
                                  barcode1 == barcode2 ~ "Same Barcode Different Site",
                                      TRUE ~ "Different Barcode Different Site"
                                     )) %>% 
  dplyr::select(Sample1, Sample2, value , Distance.type) %>%
  filter(Sample1 != Sample2) -> all.distances.to.plot.post

# Checking all went well
sapply(all.distances.to.plot.post, function(x) summary(is.na(x)))

all.distances.to.plot.post$Distance.type <- all.distances.to.plot.post$Distance.type  %>% fct_relevel( "PCR.replicates", "Jar.rep", "Same Barcode Same Year","Same Barcode Different Site","Different Barcode Different Site")

  ggplot (all.distances.to.plot.post , aes (fill = Distance.type, x = value,after_stat(density))) +
  geom_histogram(stat = 'bin', alpha = 0.9, binwidth = 0.01) + #xlim(0, 1) +
  facet_wrap( ~ Distance.type) +
 labs (x = "Pairwise Dissimilarity", y = "Density" ,
        fill = "Groups", title = "eDNA Pairwise Dissimilarity Post Occ") +theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank())
```

```{r, results="hide",warning=FALSE}
# Instead of chosing based on the pairwise distances, we will use distance to centroid

#Need to Remove Single Sampels
cleaned.tibble.post_occ.9  %>% 
  group_by(Location,Miseq_run) %>% 
 dplyr::summarise(cases = n_distinct(sample_unique)) %>% 
  filter(., cases == 1) %>% 
  unite(col="location_id", Miseq_run,Location, remove = FALSE, sep=":") %>%
  dplyr::select(location_id) -> singles
#Currently this method does not filter out these single tech reps. There are only 3

#Nest Data
cleaned.tibble.post_occ.9  %>% 
  unite(col="location_id", Miseq_run,Location, remove = FALSE, sep=":") %>% 
  filter(., !location_id %in% singles$location_id) %>% 
  group_by(Location,Miseq_run) %>% nest() -> nested.cleaning

#Calculate Similarity matrix
nested.cleaning %>% 
    mutate(matrix = map(data, tibble_to_matrix)) -> nested.cleaning

# Convert
nested.cleaning %>% mutate(ncomparisons = map(matrix, length)) -> nested.cleaning

#Function for calculating distance to centroid
dist_to_centroid <- function (x,y) {
  biol <- rep(y, dim(x)[[1]])
  
  if (length(biol) == 1) {
    output = rep(x[1]/2,2)
    names(output) <- attr(x, "Labels")
  }else{ 
    
  dispersion <- betadisper(x, group = biol)
  output = dispersion$distances
  }
  output
}

#Calculate distances to centroid
nested.cleaning <- nested.cleaning %>% mutate(distances = map2(matrix, Location, dist_to_centroid))
unlist (nested.cleaning$distances) -> all_distances.calcofi #unnest data

all_distances.calcofi

#Calculate normal distribution of distances to centroid
normparams.calcofi <- MASS::fitdistr(all_distances.calcofi, "normal")$estimate

#Calculate Probability
probs.calcofi <- pnorm(all_distances.calcofi, normparams.calcofi[1], normparams.calcofi[2])

#Determine Outliers
outliers.calcofi <- which(probs.calcofi>0.99)

#Remove Outliers
discard.calcofi <-names(all_distances.calcofi[outliers.calcofi])

to_write_discarded.calcofi <- tibble(sample = discard.calcofi,
                             distance = all_distances.calcofi[outliers.calcofi])

to_write_discarded.calcofi <- to_write_discarded.calcofi %>% left_join(tibble(sample = discard.calcofi,
                                                              probs = probs.calcofi[outliers.calcofi]))
write_csv(to_write_discarded.calcofi ,"calcofi.discared_samples.csv")

#Major Concern here is that we lost a whole 1998 sample. For the record this sample did struggle to amplify via PCR and apparently at some point in the early 2000s it had completely evaporated. Such is life

# PLot who passes this filter

all_distances.calcofi %>%
  as.tibble() %>% 
  mutate(sample = names(all_distances.calcofi)) %>% 
  filter(!sample %in% to_write_discarded.calcofi$sample) %>% 
  left_join(cleaned.tibble.post_occ.9, by=c("sample"="sample_unique")) %>% 
  dplyr::group_by(Year,Sta_ID) %>% 
  dplyr::summarise(cases = n_distinct(sample)) %>% 
  ggplot()+
  geom_raster(aes(x= Sta_ID, y = Year, fill = cases))+
  geom_text(aes(x= Sta_ID, y = Year, label = cases),color="white") +
  ggtitle("Samples per Year and Sta_ID")
  
```

```{r Step 5 Decontamination}

ASV.nested$Step3.tibble.9[[1]] %>% 
  mutate(., MiFish= str_detect(seq_number,"nextseq")) %>% 
     mutate(., Seb = str_detect(seq_number,"seb")) %>% 
     mutate(barcode = if_else(MiFish=="FALSE","Sebastes","MiFish")) %>% 
     unite(col="sample2", barcode,sample, remove = FALSE, sep=":") %>% 
 filter(.,! sample2 %in% to_write_discarded.calcofi$sample)

ASV.nested %>% 
  mutate (Step3.tibble.9_edited = purrr::map(Step3.tibble.9, 
                              function(.x){
                                .x %>%
                                mutate(., MiFish= str_detect(seq_number,"nextseq")) %>% 
     mutate(., Seb = str_detect(seq_number,"seb")) %>% 
     mutate(barcode = if_else(MiFish=="FALSE","Sebastes","MiFish")) %>% 
     unite(col="sample2", barcode,sample, remove = FALSE, sep=":")
                                }) ) -> ASV.nested


#Filter Sample
ASV.nested %>% 
  mutate(Step4.tibble = map (Step3.tibble.9_edited,  ~ filter(.,! sample2 %in% to_write_discarded.calcofi$sample))) -> ASV.nested


#Visualize Results of Clearence Process 4
ASV.nested %>% 
  transmute(Miseq_run, Summary.1 = purrr::map(Step4.tibble, ~ how.many(ASVtable = .,round ="5.Dissimilarity"))) %>% 
  left_join(ASV.summary) %>%
  mutate(Summary   = map2(Summary, Summary.1, bind_rows)) %>%
  dplyr::select(-Summary.1) -> ASV.summary


ASV.summary$Summary[[1]] %>%  kable()
ASV.summary %>% 
  dplyr::select(Miseq_run,Summary) %>% 
  unnest(Summary) %>% 
  group_by(Stage,Stat) %>% 
  summarise(sum =sum(number))
#Discarded the vast majority of ASVs, but retained most of the reads

```


#Code for merging ASV tables
```{r}

#Hashes Unique Species
Hash.key %>% 
  distinct(.,sum.taxonomy) -> hashes_unique

hashes_unique$number <- row.names(hashes_unique)
hashes_unique$number <- paste0("taxon_",hashes_unique$number)
row.names(hashes_unique)<-hashes_unique$number

Hash.key %>% 
  left_join(hashes_unique, by="sum.taxonomy") -> Hash.key.updated

head(Hash.key.updated)

#Create Data List for merging taxon files
Hash.key.updated %>% 
  mutate(Seq_number=seq_number) -> Hash.key.updated

head(Hash.key.updated)
```

###Pre Occupancy Merge, All PCR Tech Reps Separate Samples
```{r}

Hash.key.updated$number %>% unique() -> total_taxa

ASV.nested$Step2.tibble[[1]] %>% 
  mutate(miseq = ASV.nested$Miseq_run[[1]]) %>% 
  unite(miseq,sample, col="Sample") %>% 
  mutate(Seq_number=Hash) %>% 
  left_join(Hash.key.updated, by="Seq_number") %>% 
  dplyr::group_by(number,Sample) %>%
  dplyr::summarise(nReads=sum(nReads)) %>% 
  spread(., Sample, nReads) %>% #convert to wide data format
  replace(is.na(.), 0) -> nextseq_b
nextseq_b$number %>%  unique() -> nextseq_b_taxa


ASV.nested$Step2.tibble[[2]] %>% 
  mutate(miseq = ASV.nested$Miseq_run[[2]]) %>% 
  unite(miseq,sample, col="Sample") %>% 
  mutate(Seq_number=Hash) %>% 
  left_join(Hash.key.updated, by="Seq_number") %>% 
  dplyr::group_by(number,Sample) %>%
  dplyr::summarise(nReads=sum(nReads)) %>% 
  spread(., Sample, nReads) %>% #convert to wide data format
  replace(is.na(.), 0) -> seb_c
seb_c$number %>%  unique() -> seb_c_taxa


total_kept_taxa <- (append(nextseq_b_taxa,seb_c_taxa)) %>% unique()


nextseq_b %>% ungroup() %>% 
  add_row(number=setdiff(total_kept_taxa,nextseq_b_taxa)) %>% 
  arrange(number) %>% 
  replace(is.na(.), 0) -> nextseq_b

seb_c %>% ungroup() %>% 
  add_row(number=setdiff(total_kept_taxa,seb_c_taxa)) %>% 
  arrange(number) %>% 
  replace(is.na(.), 0) -> seb_c

nextseq_b <- as.data.frame(nextseq_b)
row.names(nextseq_b) <- nextseq_b$number
nextseq_b %>% ungroup() %>% dplyr::select(-number) -> nextseq_b

seb_c <- as.data.frame(seb_c)
row.names(seb_c) <- seb_c$number
seb_c %>% ungroup() %>% dplyr::select(-number) -> seb_c

dim(nextseq_b)
dim(seb_c)

rownames(nextseq_b)
rownames(seb_c)


colnames(nextseq_b)
colnames(seb_c)

#first, we want to create proportions by dividing by the rowsums:
#we could do this with sweep() or mutate_all() or other ways, but using vegan:

nextseq_b_prop <- decostand(nextseq_b, method = "total", MARGIN = 2)
seb_c_prop <- decostand(seb_c, method = "total", MARGIN = 2)

#second, we want to ask how the proprortion for each species has changed across columns (samples). 
#We do this by scaling everything to the max observed in each row. 

#to do this WITHIN a dataset, we could just do (again, using vegan):
nextseq_b_index <- decostand(nextseq_b_prop, method = "max", MARGIN = 1)
seb_c_index <- decostand(seb_c_prop, method = "max", MARGIN = 1)

#this gives us an index between 0 and 1 for each species in each dataset.  

#But if we want to combine datasets, this second step has to happen in the combined dataset, so it all gets scaled to 0-1.  
#easy enough:

combined_index <- decostand(cbind(nextseq_b_prop,seb_c_prop), method = "max", MARGIN = 1)
#now both datasets are combined, on a common, comparable scale.
```

```{r}
results_calcofi_reads = cbind(nextseq_b,seb_c)

Hash.key.updated.2 <- Hash.key.updated[!duplicated(Hash.key.updated$number), ]

results_calcofi_reads$number <- rownames(results_calcofi_reads)

results_calcofi_reads %>% 
  left_join(Hash.key.updated.2, by="number") %>% 
  dplyr::select(-number,-seq_number,-Seq_number) -> results_calcofi_reads
results_calcofi_reads$sum.taxonomy
saveRDS(results_calcofi_reads,file="pre_occupancy_results_merged_runs_separate_read_counts.RDS")
write_csv(results_calcofi_reads ,"ASV_pre_occ_sum_taxonomy_read_counts_runs_separate.csv")

```


```{r}

Hash.key.updated.2 <- Hash.key.updated[!duplicated(Hash.key.updated$number), ]

combined_index$number <- rownames(combined_index)

combined_index %>% 
  left_join(Hash.key.updated.2, by="number") %>% 
  dplyr::select(-number,-seq_number,-Seq_number) -> combined_index

saveRDS(combined_index,file="pre_occupancy_results_merged_runs_separate_eDNA_index.RDS")
write_csv(combined_index ,"ASV_pre_occ_sum_taxonomy_edna_index_runs_separate.csv")

combined_index%>%  as.data.frame()%>%
  pivot_longer(., names_to="sample", cols=`nextseq_1996_4_80_60_1_1`:`seb_2019_4_93.3_60_1_3`,values_to="eIDX") %>% 
  group_by(sum.taxonomy) %>% 
  summarise(max(eIDX)) %>%  View()
```

###Post Occupancy Merge, All PCR Tech Reps Separate Samples
```{r}

Hash.key.updated$number %>% unique() -> total_taxa


ASV.nested$Step4.tibble[[1]] %>% 
  mutate(miseq = ASV.nested$Miseq_run[[1]]) %>% 
  unite(miseq,sample, col="Sample") %>% 
  mutate(Seq_number=Hash) %>% 
  left_join(Hash.key.updated, by="Seq_number") %>% 
  dplyr::group_by(number,Sample) %>%
  dplyr::summarise(nReads=sum(nReads)) %>% 
  spread(., Sample, nReads) %>% #convert to wide data format
  replace(is.na(.), 0) -> nextseq_b
nextseq_b$number %>%  unique() -> nextseq_b_taxa


ASV.nested$Step4.tibble[[2]] %>% 
  mutate(miseq = ASV.nested$Miseq_run[[2]]) %>% 
  unite(miseq,sample, col="Sample") %>% 
  mutate(Seq_number=Hash) %>% 
  left_join(Hash.key.updated, by="Seq_number") %>% 
  dplyr::group_by(number,Sample) %>%
  dplyr::summarise(nReads=sum(nReads)) %>% 
  spread(., Sample, nReads) %>% #convert to wide data format
  replace(is.na(.), 0) -> seb_c
seb_c$number %>%  unique() -> seb_c_taxa


total_kept_taxa <- append(nextseq_b_taxa,seb_c_taxa) %>% unique()

nextseq_b %>% ungroup() %>% 
  add_row(number=setdiff(total_kept_taxa,nextseq_b_taxa)) %>%
    arrange(number) %>% 
  replace(is.na(.), 0) -> nextseq_b

seb_c %>% ungroup() %>% 
  add_row(number=setdiff(total_kept_taxa,seb_c_taxa)) %>% 
    arrange(number) %>% 
  replace(is.na(.), 0) -> seb_c

nextseq_b <- as.data.frame(nextseq_b)
row.names(nextseq_b) <- nextseq_b$number
nextseq_b %>% ungroup() %>% dplyr::select(-number) -> nextseq_b

seb_c <- as.data.frame(seb_c)
row.names(seb_c) <- seb_c$number
seb_c %>% ungroup() %>% dplyr::select(-number) -> seb_c

dim(nextseq_b)
dim(seb_c)

rownames(nextseq_b)
rownames(seb_c)


colnames(nextseq_b)
colnames(seb_c)

#first, we want to create proportions by dividing by the rowsums:
#we could do this with sweep() or mutate_all() or other ways, but using vegan:

nextseq_b_prop <- decostand(nextseq_b, method = "total", MARGIN = 2)
seb_c_prop <- decostand(seb_c, method = "total", MARGIN = 2)

#second, we want to ask how the proprortion for each species has changed across columns (samples). 
#We do this by scaling everything to the max observed in each row. 

#to do this WITHIN a dataset, we could just do (again, using vegan):
nextseq_b_index <- decostand(nextseq_b_prop, method = "max", MARGIN = 1)
seb_c_index <- decostand(seb_c_prop, method = "max", MARGIN = 1)

#this gives us an index between 0 and 1 for each species in each dataset.  

#But if we want to combine datasets, this second step has to happen in the combined dataset, so it all gets scaled to 0-1.  
#easy enough:

combined_index <- decostand(cbind(nextseq_b_prop,seb_c_prop), method = "max", MARGIN = 1)
#now both datasets are combined, on a common, comparable scale.
```

```{r}

results_calcofi_reads = cbind(nextseq_b,seb_c)

Hash.key.updated.2 <- Hash.key.updated[!duplicated(Hash.key.updated$number), ]

results_calcofi_reads$number <- rownames(results_calcofi_reads)

results_calcofi_reads %>% 
  left_join(Hash.key.updated.2, by="number") %>% 
  dplyr::select(-number,-seq_number,-Seq_number) -> results_calcofi_reads
results_calcofi_reads$sum.taxonomy
saveRDS(results_calcofi_reads,file="post_occupancy_results_merged_runs_separate_read_counts.RDS")
write_csv(results_calcofi_reads ,"ASV_post_occ_sum_taxonomy_read_counts_runs_separate.csv")

```


```{r}

Hash.key.updated.2 <- Hash.key.updated[!duplicated(Hash.key.updated$number), ]

combined_index$number <- rownames(combined_index)

combined_index %>% 
  left_join(Hash.key.updated.2, by="number") %>% 
  dplyr::select(-number,-seq_number,-Seq_number) -> combined_index
combined_index$sum.taxonomy
saveRDS(combined_index,file="post_occupancy_results_merged_runs_separate_eDNA_index.RDS")
write_csv(combined_index ,"ASV_post_occ_sum_taxonomy_edna_index_runs_separate.csv")
```

#Code for Merging Tech Reps

###Pre Occupancy Merge, Bio reps sep
```{r}

ASV.nested$Step2.tibble[[1]] %>% 
  mutate(Sample = sample) %>% 
  mutate(Seq_number=Hash) %>%
  left_join(Hash.key.updated, by="Seq_number") %>% 
  dplyr::group_by(number,Sample) %>%
  dplyr::summarise(nReads=sum(nReads)) %>% 
  spread(., Sample, nReads) %>% #convert to wide data format
  replace(is.na(.), 0)  -> nextseq_b
nextseq_b$number %>%  unique() -> nextseq_b_taxa

metadata %>% 
  filter(., !(sample2 %in% controls)) %>% 
  filter(.,!(sample2 %in% colnames(nextseq_b))) %>% 
  pull(sample2) %>%  unique()-> columns2add

nextseq_b <- as.data.frame(nextseq_b)

nextseq_b %>% 
     tibble::add_column(!!!set_names(as.list(rep(NA, length(columns2add))),nm=columns2add)) %>% 
     replace(is.na(.), 0) %>% 
  select(sort(current_vars()))-> nextseq_b

row.names(nextseq_b) <- nextseq_b$number
nextseq_b %>% ungroup() -> nextseq_b

ASV.nested$Step2.tibble[[2]] %>% 
  mutate(Sample = sample) %>% 
  mutate(Seq_number=Hash) %>%
  left_join(Hash.key.updated, by="Seq_number") %>% 
  dplyr::group_by(number,Sample) %>%
  dplyr::summarise(nReads=sum(nReads)) %>% 
  spread(., Sample, nReads) %>% #convert to wide data format
  replace(is.na(.), 0)  -> seb_c
seb_c$number %>%  unique() -> seb_c_taxa

metadata %>% 
  filter(., !(sample2 %in% controls)) %>% 
  filter(.,!(sample2 %in% colnames(seb_c))) %>% 
  pull(sample2) %>%  unique()-> columns2add

seb_c <- as.data.frame(seb_c)

seb_c %>% 
     tibble::add_column(!!!set_names(as.list(rep(NA, length(columns2add))),nm=columns2add)) %>% 
     replace(is.na(.), 0) %>% 
  select(sort(current_vars())) -> seb_c

row.names(seb_c) <- seb_c$number
seb_c %>% ungroup() -> seb_c

total_kept_taxa <- (append(nextseq_b_taxa,seb_c_taxa)) %>% unique()

nextseq_b %>% ungroup() %>% 
  add_row(number=setdiff(total_kept_taxa,nextseq_b_taxa)) %>% 
  arrange(number) %>% 
  replace(is.na(.), 0) -> nextseq_b

seb_c %>% ungroup() %>% 
  add_row(number=setdiff(total_kept_taxa,seb_c_taxa)) %>% 
  arrange(number) %>% 
  replace(is.na(.), 0) -> seb_c

nextseq_b <- as.data.frame(nextseq_b)
row.names(nextseq_b) <- nextseq_b$number
nextseq_b %>% ungroup() %>% dplyr::select(-number) -> nextseq_b

seb_c <- as.data.frame(seb_c)
row.names(seb_c) <- seb_c$number
seb_c %>% ungroup() %>% dplyr::select(-number) -> seb_c

dim(nextseq_b)
dim(seb_c)

colnames(nextseq_b)
colnames(seb_c)

rownames(nextseq_b)
rownames(seb_c)

nextseq_b+seb_c -> combined_df

#first, we want to create proportions by dividing by the rowsums:
#we could do this with sweep() or mutate_all() or other ways, but using vegan:

combined_df_prop <- decostand(combined_df, method = "total", MARGIN = 2)

#second, we want to ask how the proprortion for each species has changed across columns (samples). 
#We do this by scaling everything to the max observed in each row. 

#to do this WITHIN a dataset, we could just do (again, using vegan):
#eDNA Index between 0-1 made by straight adding reads across each decontaminated datatable
combined_df_index <- decostand(combined_df_prop, method = "max", MARGIN = 1)
dim(combined_df_index)

```

```{r}

Hash.key.updated.2 <- Hash.key.updated[!duplicated(Hash.key.updated$number), ]

combined_df$number <- rownames(combined_df)

combined_df %>% 
  left_join(Hash.key.updated.2, by="number") %>% 
  dplyr::select(-number,-seq_number,-Seq_number) -> combined_df
combined_df$sum.taxonomy

saveRDS(combined_df,file="calcofi_pre_occ_tech_averaged_sum.taxonomy_reads.RDS")
write_csv(combined_df,"calcofi_pre_occ_tech_averagedsum.taxonomy_reads.csv")

```

```{r}

Hash.key.updated.2 <- Hash.key.updated[!duplicated(Hash.key.updated$number), ]

combined_df_index$number <- rownames(combined_df_index)

combined_df_index %>% 
  left_join(Hash.key.updated.2, by="number") %>% 
  dplyr::select(-number,-seq_number,-Seq_number) -> combined_df_index
combined_df_index$sum.taxonomy

saveRDS(combined_df_index,file="calcofi_pre_occ_tech_averaged_sum.taxonomy_e_index.RDS")
write_csv(combined_df_index,"calcofi_pre_occ_tech_averagedsum.taxonomy_e_index.csv")
```

###Post Occupancy Merge, Bio reps sep
```{r}

ASV.nested$Step4.tibble[[1]] %>% 
  mutate(Sample = sample) %>% 
  mutate(Seq_number=Hash) %>%
  left_join(Hash.key.updated, by="Seq_number") %>% 
  dplyr::group_by(number,Sample) %>%
  dplyr::summarise(nReads=sum(nReads)) %>% 
  spread(., Sample, nReads) %>% #convert to wide data format
  replace(is.na(.), 0)  -> nextseq_b
nextseq_b$number %>%  unique() -> nextseq_b_taxa

metadata %>% 
  filter(., !(sample2 %in% controls)) %>% 
  filter(.,!(sample2 %in% colnames(nextseq_b))) %>% 
  pull(sample2) %>%  unique()-> columns2add

nextseq_b <- as.data.frame(nextseq_b)

nextseq_b %>% 
     tibble::add_column(!!!set_names(as.list(rep(NA, length(columns2add))),nm=columns2add)) %>% 
     replace(is.na(.), 0) %>% 
  select(sort(current_vars()))-> nextseq_b

row.names(nextseq_b) <- nextseq_b$number
nextseq_b %>% ungroup() -> nextseq_b

ASV.nested$Step4.tibble[[2]] %>% 
  mutate(Sample = sample) %>% 
  mutate(Seq_number=Hash) %>%
  left_join(Hash.key.updated, by="Seq_number") %>% 
  dplyr::group_by(number,Sample) %>%
  dplyr::summarise(nReads=sum(nReads)) %>% 
  spread(., Sample, nReads) %>% #convert to wide data format
  replace(is.na(.), 0)  -> seb_c
seb_c$number %>%  unique() -> seb_c_taxa

metadata %>% 
  filter(., !(sample2 %in% controls)) %>% 
  filter(.,!(sample2 %in% colnames(seb_c))) %>% 
  pull(sample2) %>%  unique()-> columns2add
 
seb_c <- as.data.frame(seb_c)

seb_c %>% 
     tibble::add_column(!!!set_names(as.list(rep(NA, length(columns2add))),nm=columns2add)) %>% 
     replace(is.na(.), 0) %>% 
  select(sort(current_vars())) -> seb_c

row.names(seb_c) <- seb_c$number
seb_c %>% ungroup() -> seb_c

total_kept_taxa <- (append(nextseq_b_taxa,seb_c_taxa)) %>% unique()

nextseq_b %>% ungroup() %>% 
  add_row(number=setdiff(total_kept_taxa,nextseq_b_taxa)) %>% 
  arrange(number) %>% 
  replace(is.na(.), 0) -> nextseq_b

seb_c %>% ungroup() %>% 
  add_row(number=setdiff(total_kept_taxa,seb_c_taxa)) %>% 
  arrange(number) %>% 
  replace(is.na(.), 0) -> seb_c

nextseq_b <- as.data.frame(nextseq_b)
row.names(nextseq_b) <- nextseq_b$number
nextseq_b %>% ungroup() %>% dplyr::select(-number) -> nextseq_b

seb_c <- as.data.frame(seb_c)
row.names(seb_c) <- seb_c$number
seb_c %>% ungroup() %>% dplyr::select(-number) -> seb_c

dim(nextseq_b)
dim(seb_c)

colnames(nextseq_b)
colnames(seb_c)

rownames(nextseq_b)
rownames(seb_c)


nextseq_b+seb_c -> combined_df

#first, we want to create proportions by dividing by the rowsums:
#we could do this with sweep() or mutate_all() or other ways, but using vegan:

combined_df_prop <- decostand(combined_df, method = "total", MARGIN = 2)

#second, we want to ask how the proprortion for each species has changed across columns (samples). 
#We do this by scaling everything to the max observed in each row. 

#to do this WITHIN a dataset, we could just do (again, using vegan):
#eDNA Index between 0-1 made by straight adding reads across each decontaminated datatable
combined_df_index <- decostand(combined_df_prop, method = "max", MARGIN = 1)
dim(combined_df_index)

```

```{r}

Hash.key.updated.2 <- Hash.key.updated[!duplicated(Hash.key.updated$number), ]

combined_df$number <- rownames(combined_df)

combined_df %>% 
  left_join(Hash.key.updated.2, by="number") %>% 
  dplyr::select(-number,-seq_number,-Seq_number) -> combined_df
combined_df$sum.taxonomy

saveRDS(combined_df,file="calcofi_post_occ_tech_averaged_sum.taxonomy_reads.RDS")
write_csv(combined_df,"calcofi_post_occ_tech_averagedsum.taxonomy_reads.csv")

```

```{r}

Hash.key.updated.2 <- Hash.key.updated[!duplicated(Hash.key.updated$number), ]

combined_df_index$number <- rownames(combined_df_index)

combined_df_index %>% 
  left_join(Hash.key.updated.2, by="number") %>% 
  dplyr::select(-number,-seq_number,-Seq_number) -> combined_df_index
combined_df_index$sum.taxonomy

saveRDS(combined_df_index,file="calcofi_post_occ_tech_averaged_sum.taxonomy_e_index.RDS")
write_csv(combined_df_index,"calcofi_post_occ_tech_averagedsum.taxonomy_e_index.csv")

combined_df_index%>%  as.data.frame()%>%
  pivot_longer(., names_to="sample", cols=`1996_4_80_60_1_1`:`2019_4_93.3_60_1_3`,values_to="eIDX") %>%
  group_by(sum.taxonomy) %>% 
  summarise(max(eIDX)) %>%  View()
```


#Code for Merging Sites

###Pre Occupancy Merge by Site
```{r}
ASV.nested %>% 
  dplyr::select(Step2.tibble,Miseq_run) %>% 
  unnest(Step2.tibble) %>% 
  mutate(Sample = sample) %>% 
  mutate(Seq_number=Hash) %>%
  left_join(Hash.key.updated, by="Seq_number") %>% 
  mutate(., Barcode = case_when(Miseq_run == "nextseq"~"MiFish",
                                Miseq_run == "seb"~"Sebastes")) %>%
  mutate(., Sample = recode(Sample, `2019_4_80_60_J1_1_1`="2019_4_80_60_1_1",
                            `2019_4_80_60_J1_1_2`="2019_4_80_60_1_2",
                            `2019_4_80_60_J1_1_3`="2019_4_80_60_1_3",
                            `2019_4_80_60_J2_2_1`="2019_4_80_60_1_1",
                            `2019_4_80_60_J2_2_2`="2019_4_80_60_1_2",
                            `2019_4_80_60_J2_2_3`="2019_4_80_60_1_3")) %>% 
  left_join(metadata, by=c("Barcode","Sample"="sample2")) %>% 
  dplyr::group_by(sum.taxonomy,Location) %>%
  dplyr::summarise(nReads=sum(nReads)) %>% 
  spread(., Location, nReads) %>% #convert to wide data format
  replace(is.na(.), 0)  -> pre_wide_reads

saveRDS(pre_wide_reads,file="calcofi_pre_occ_site_averaged_sum.taxonomy_reads.RDS")
write_csv(pre_wide_reads ,"calcofi_pre_occ_site_averaged_sum.taxonomy_reads.csv")

ASV.nested %>% 
  dplyr::select(Step2.tibble,Miseq_run) %>% 
  unnest(Step2.tibble) %>% 
  mutate(Sample = sample) %>% 
  mutate(Seq_number=Hash) %>%
  left_join(Hash.key.updated, by="Seq_number") %>% 
   mutate(., Barcode = case_when(Miseq_run == "nextseq"~"MiFish",
                                Miseq_run == "seb"~"Sebastes")) %>%
  mutate(., Sample = recode(Sample, `2019_4_80_60_J1_1_1`="2019_4_80_60_1_1",
                            `2019_4_80_60_J1_1_2`="2019_4_80_60_1_2",
                            `2019_4_80_60_J1_1_3`="2019_4_80_60_1_3",
                            `2019_4_80_60_J2_2_1`="2019_4_80_60_1_1",
                            `2019_4_80_60_J2_2_2`="2019_4_80_60_1_2",
                            `2019_4_80_60_J2_2_3`="2019_4_80_60_1_3")) %>% 
  left_join(metadata, by=c("Barcode","Sample"="sample2")) %>% 
  ungroup() %>% 
  group_by(Location, sum.taxonomy) %>% 
  summarise(sumreads = sum(nReads)) %>% 
  dplyr::group_by(Location) %>%
  mutate (Tot = sum(sumreads),
          Row.sums = sumreads / Tot) %>% 
  dplyr::group_by (sum.taxonomy) %>%
  mutate (Colmax = max (Row.sums),
          Normalized.reads = Row.sums / Colmax) %>% 
  ungroup() %>% 
  dplyr::select(Location,Normalized.reads, sum.taxonomy) %>% 
  spread(., Location, Normalized.reads) %>% #convert to wide data format
  replace(is.na(.), 0)  -> pre_wide

saveRDS(pre_wide,file="calcofi_pre_occ_site_averaged_sum.taxonomy_e_index.RDS")
write_csv(pre_wide,"calcofi_pre_occ_site_averaged_sum.taxonomy_e_index.csv")

```

###Post Occupancy Merge by Site
```{r}

ASV.nested %>% 
  dplyr::select(Step4.tibble,Miseq_run) %>% 
  unnest(Step4.tibble) %>% 
  mutate(Sample = sample) %>% 
  mutate(Seq_number=Hash) %>%
  left_join(Hash.key.updated, by="Seq_number") %>% 
  mutate(., Barcode = case_when(Miseq_run == "nextseq"~"MiFish",
                                Miseq_run == "seb"~"Sebastes")) %>%
  mutate(., Sample = recode(Sample, `2019_4_80_60_J1_1_1`="2019_4_80_60_1_1",
                            `2019_4_80_60_J1_1_2`="2019_4_80_60_1_2",
                            `2019_4_80_60_J1_1_3`="2019_4_80_60_1_3",
                            `2019_4_80_60_J2_2_1`="2019_4_80_60_1_1",
                            `2019_4_80_60_J2_2_2`="2019_4_80_60_1_2",
                            `2019_4_80_60_J2_2_3`="2019_4_80_60_1_3")) %>% 
  left_join(metadata, by=c("Barcode","Sample"="sample2")) %>% 
  ungroup() %>% 
  dplyr::group_by(sum.taxonomy.y,Location) %>%
  dplyr::summarise(nReads=sum(nReads)) %>% 
  spread(., Location, nReads) %>% #convert to wide data format
  replace(is.na(.), 0)  -> post_wide_reads

saveRDS(post_wide_reads,file="calcofi_post_occ_site_averaged_sum.taxonomy_reads.RDS")
write_csv(post_wide_reads ,"calcofi_post_occ_site_averaged_sum.taxonomy_reads.csv")

ASV.nested %>% 
  dplyr::select(Step4.tibble,Miseq_run) %>% 
  unnest(Step4.tibble) %>% 
  mutate(Sample = sample) %>% 
  mutate(Seq_number=Hash) %>%
  left_join(Hash.key.updated, by="Seq_number") %>% 
   mutate(., Barcode = case_when(Miseq_run == "nextseq"~"MiFish",
                                Miseq_run == "seb"~"Sebastes")) %>%
  mutate(., Sample = recode(Sample, `2019_4_80_60_J1_1_1`="2019_4_80_60_1_1",
                            `2019_4_80_60_J1_1_2`="2019_4_80_60_1_2",
                            `2019_4_80_60_J1_1_3`="2019_4_80_60_1_3",
                            `2019_4_80_60_J2_2_1`="2019_4_80_60_1_1",
                            `2019_4_80_60_J2_2_2`="2019_4_80_60_1_2",
                            `2019_4_80_60_J2_2_3`="2019_4_80_60_1_3")) %>% 
  left_join(metadata, by=c("Barcode","Sample"="sample2")) %>% 
  ungroup() %>% 
  group_by(Location, sum.taxonomy.y) %>% 
  summarise(sumreads = sum(nReads)) %>% 
  dplyr::group_by(Location) %>%
  mutate (Tot = sum(sumreads),
          Row.sums = sumreads / Tot) %>% 
  dplyr::group_by (sum.taxonomy.y) %>%
  mutate (Colmax = max (Row.sums),
          Normalized.reads = Row.sums / Colmax) %>% 
  dplyr::select(Location,Normalized.reads, sum.taxonomy=sum.taxonomy.y) %>% 
  spread(., Location, Normalized.reads) %>% #convert to wide data format
  replace(is.na(.), 0)  -> post_wide


saveRDS(post_wide,file="calcofi_post_occ_site_averaged_sum.taxonomy_e_index.RDS")
write_csv(post_wide,"calcofi_post_occ_site_averaged_sum.taxonomy_e_index.csv")


post_wide %>% 
  as.data.frame( )%>%
  pivot_longer(., names_to="sample", cols=`1996_4_80_60`:`2019_4_93.3_60`,values_to="eIDX") %>%
  group_by(sum.taxonomy) %>% 
  summarise(max(eIDX)) %>%  View()
  
```
